### 2024-10-20 paper/paper.qmd
Update paper and delete unnecessary files

---
title: "Predicting the 2024 US Presidential Election with a Model-Based Forecast"
subtitle: "Using Generalized Linear Models to Predict Election Outcomes"
author: 
  - Yuanyi (Leo) Liu
  - Dezhen Chen
  - Ziyuan Shen
thanks: "Code and data are available at: [Forecasting the 2024 US Presidential Election](https://github.com/leoyliu/Forecasting-the-2024-US-Presidential-Election)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-10-20 scripts/07-install_packages copy.R

@@ -1,0 +1,17 @@
+#### Preamble ####
+# Purpose: Install necessary packages
+# Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
+# Date: 26 September 2024
+# Contact: leoy.liu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+# Any other information needed? None
+
+
+#### Install packages ####
+install.packages("tidyverse")
+install.packages("arrow")
+install.packages("here")
+install.packages("kableExtra")
+install.packages("opendatatoronto")
+install.packages("janitor")

### 2024-10-21 scripts/02-download_data.R
Update scripts

@@ -9,18 +9,17 @@
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
+raw_elections_data <-
+  read_csv(
+    file = 
+      "https://projects.fivethirtyeight.com/polls/data/president_polls.csv",
+    show_col_types = TRUE
+  )
 
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
-
-         
+write_csv(raw_elections_data, "data/01-raw_data/raw_data.csv") 

### 2024-10-21 scripts/03-clean_data.R

@@ -11,7 +11,7 @@
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 
 cleaned_data <-
   raw_data |>

### 2024-10-21 scripts/03-clean_data.R
clean data

@@ -16,29 +16,8 @@ raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+  filter(numeric_grade >= 3.0, candidate_name == "Kamala Harris") |>
+  select(poll_id, display_name, state, internal, partisan, race_id, pct)
 
 #### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")

### 2024-10-21 paper/paper.qmd
update data section

@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+We use the statistical programming language R [@citeR] to process and analyze polling data for the 2024 US Presidential election.
+The data, obtained from a repository of publicly available polls, includes variables from numerous pollsters across the country [@citedata].
+The aim is to create a reproducible forecast model by focusing on high-quality polls and narrowing our scope to Kamala Harris as a candidate of interest.
+Following methodologies discussed by "Telling Stories with Data" [@tellingstories], we examine how polling data reflects electoral behavior and voter preferences.
 
-Overview text
+The dataset includes 15,891 rows and 52 columns, covering various pollster attributes such as pollster name, state, methodology, and polling results.
+We filter the dataset to include only high-quality polls, i.e., those with a numeric grade of 3.0 or higher, ensuring that only reputable and well-documented pollster results are used in our model.
+Additionally, we focus solely on polls that include Kamala Harris as a candidate, which helps narrow our analysis to a specific electoral scenario.
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+Polling data captures voter preferences and electoral forecasts by collecting responses from a representative sample of the population.
+In this case, pollsters attempt to gauge public opinion by surveying individuals on their preferred candidate, adjusting for demographic factors and political trends.
+The raw data entries reflect the outcomes of these surveys.
+
+Pollsters often rely on random sampling methods to recruit participants, as discussed in [@ todo], ensuring a diverse and representative group.
+Some pollsters use online platforms, while others use phone interviews or in-person surveys.
+The dataset captures these variations through variables such as `methodology` and `sample_size`.
+Sampling errors, response biases, and adjustments (e.g., weighting respondents based on age, race, or geographic region) are part of how this world phenomenon is translated into data entries.
+
+The process begins with identifying the population of interest—likely voters or registered voters—and applying statistical adjustments to the raw responses.
+Pollsters handle non-response through weighting or imputation methods, ensuring that missing data or low response rates do not skew the results significantly.
+The column `numeric_grade` reflects how well these pollsters adhere to rigorous methodology, allowing us to filter for only the most reliable sources in our analysis.
 
@@
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+### Percent Support (pct)
+The primary outcome variable in this dataset is the percentage of respondents who support a given candidate.
+This is represented by the pct variable, which is reported by pollsters for each candidate they survey.
+For Kamala Harris, this percentage reflects her standing in polls, and variations in this metric can indicate shifts in voter preference over time.
+
+Below is a summary table showing the average, minimum, and maximum percent support for Kamala Harris across high-quality polls:
 
@@
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
@@
 
-Add graphs, tables and text.
+### Pollster Name (display_name)
+This variable represents the pollster responsible for each entry in the dataset.
+Different pollsters may use varying methods and possess differing levels of reliability, which the numeric_grade helps quantify.
+High-quality pollsters (numeric_grade ≥ 3.0) are emphasized in this analysis to ensure the robustness of the forecast.
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+### Internal Polling (internal)
+The variable internal is a binary indicator that identifies whether a poll was commissioned by a political campaign or interest group.
+Internal polls can sometimes be biased, either in how respondents are selected or how results are reported.
+However, the filtering for high-quality pollsters ensures that even internal polls meet certain standards of rigor.
+
+### Partisan Polling (partisan)
+Like internal polling, partisan polling can introduce bias, as it may be sponsored by organizations with a vested interest in the election outcome.
+The partisan variable, similar to the internal variable, flags such polls.
+In the dataset, these are rare but still important to identify, especially when making impartial predictions.
+
+### Party Affiliation (party)
+The party variable indicates the political party that the poll respondent supports.
+This is key to understanding the partisan leanings of the sample.
+For Kamala Harris, her affiliation with the Democratic Party is represented in this column.
+
+Below is a table summarizing the distribution of party affiliations in polls that include Kamala Harris:
+
+### Race ID (race_id)
+This variable identifies the electoral race or contest being polled.
+In this analysis, the focus is on the 2024 presidential election.
+Tracking results across different races (i.e., primary versus general election) helps in understanding shifts in voter opinion throughout the campaign.
+
+In summary, the dataset offers a rich variety of variables that capture voter sentiment, pollster reliability, and electoral dynamics.
+By carefully filtering and analyzing this data, we can build a robust model to forecast the outcome of the 2024 US Presidential election.
 
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```
@@
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-10-23 scripts/03-clean_data.R
update cleaning data

@@ -17,7 +17,7 @@ cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
   filter(numeric_grade >= 3.0, candidate_name == "Kamala Harris") |>
-  select(poll_id, display_name, state, internal, partisan, race_id, pct)
+  select(poll_id, pollster, pollscore, transparency_score, display_name, state, race_id, pct)
 
 #### Save data ####
 write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")

### 2024-10-23 scripts/06-model_data.R
create model

@@ -13,12 +13,12 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
 ### Model data ####
 first_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
+    formula = pct ~ pollster + pollscore + transparency_score,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
@@ -27,11 +27,11 @@ first_model <-
     seed = 853
   )
 
+summary(first_model)
+
 
 #### Save model ####
 saveRDS(
   first_model,
   file = "models/first_model.rds"
 )
-
-

### 2024-10-23 scripts/03-clean_data.R
clean data and create parquet file

@@ -17,7 +17,8 @@ cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
   filter(numeric_grade >= 3.0, candidate_name == "Kamala Harris") |>
-  select(poll_id, pollster, pollscore, transparency_score, display_name, state, race_id, pct)
+  select(poll_id, pollster, pollscore, transparency_score, display_name, state, pct) |>
+  mutate(poll_type = ifelse(is.na(state), "National", "State"))  # Add new column 'poll_type'
 
 #### Save data ####
 write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")

### 2024-10-24 paper/paper.qmd
fix git issue

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "In this paper, we use a logistic regression model based on \"poll-of-polls\" data to predict the winner of the 2024 U.S.
+presidential election.
+By combining multiple polls, the model smooths out short-term fluctuations in surveys to make more reliable estimates of voter preferences.
+The findings show early trends in the leading candidates and reflect public opinion and its evolution through the election period.
+This prediction improves understanding of electoral trends and helps to explain the changing political scene more clearly"
 format: pdf
@@
 
-# Introduction
+# Introduction {#sec-intro}
 
-Overview paragraph
+The presidential election has a significant impact on national and global policies, which makes election forecasting a valuable tool for understanding political outcomes.
+However, individual polls often contain biases and short-term fluctuations that can obscure long-term trends.
+To deal with these challenges, we use a ‘poll-of-polls’ approach that combines multiple polls to provide more stable predictions of voter preferences over time.
+In this paper, we use national polling data from the period leading up to the 2024 U.S.
+presidential election to generate a logistic model that predicts the winner while capturing changes in public opinion throughout the election period.
 
-Estimand paragraph
+The model estimates the probability of a candidate winning an election based on aggregated polling data.
+Logistic regression is used for binary outcomes such as election results, which allows us to model the likelihood of each candidate winning as new data becomes available.
+By taking into account changes in opinion polls and tracking trends in public opinion over time, this model improves the accuracy of predictions.
 
-Results paragraph
+Our analysis identifies key trends among the major candidates and tracks changes in public sentiment throughout the campaign.
+The results suggest that aggregated polls can reduce some uncertainty by smoothing short-term fluctuations between surveys, but uncertainty cannot be eliminated.
+A sudden change in public opinion can still change the path of an election campaign, which highlights the importance of continuous polling monitoring.
 
-Why it matters paragraph
+A reliable election forecast can influence public expectations, and campaign strategies, and increase the visibility of reporting on election trends.
+An accurate forecast can also increase voter participation by providing individuals with a clearer perspective of the electoral landscape, and help them participate more effectively in the process of democracy.
+Prediction models like ours not only help with resource allocation for campaigns but also support the wider public by providing them with a clearer understanding of political dynamics.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+The structure of the paper is organized as follows: following @sec-intro, @sec-data presents the data collection and cleaning process, along with an overview of the variables used in the analysis.
+@sec-model introduces the forecasting models, explaining why the selected models are suitable for predicting election outcomes based on aggregated polling data.
+Then @sec-result presents the main findings, including detailed crime trends for each neighborhood and year.
+Finally, @sec-discussion provides the results, highlighting key trends and predictions.
+Eventuallt, @sec-discussion concludes with a discussion of the findings, evaluating the reliability of the forecasts and identifying potential limitations of the models.
 
@@
 
-# Model
+# Model {#sec-model}
 
@@
 
-# Results
+# Results {#sec-result}
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-10-24 paper/paper.qmd
update abstract

@@
 The findings show early trends in the leading candidates and reflect public opinion and its evolution through the election period.
-This prediction improves understanding of electoral trends and helps to explain the changing political scene more clearly"
+This prediction improves understanding of electoral trends and helps to explain the changing political scene more clearly."
 format: pdf

### 2024-10-24 paper/paper.qmd
Create model and update model section

@@
 library(palmerpenguins)
+library(modelsummary)
 ```
@@
 # Model {#sec-model}
+Our modeling approach aims to quantify the relationship between polling characteristics and the probability of Harris winning the election.
+We use a generalized linear model (GLM) to evaluate how different factors—such as poll type, polling organization, poll score, and transparency score—impact Harris' support rate.
+The model is implemented using the stan_glm function, with a Gaussian distribution applied to describe the variability in support percentages.
 
-The goal of our modelling strategy is twofold. Firstly,...
+In our analysis, we filtered the data to include only polls from organizations with a poll score above 3, ensuring the reliability of our data sources.
+We selected predictors including  poll_type, pollster, pollscore, and transparency_score.
+Since the response variable (support percentage) is continuous, we utilized a Gaussian linear regression model.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+The model assumes that the distribution of support percentage, given the polling characteristics, follows a normal distribution.
+This assumption makes the parameter estimation more straightforward and is commonly used in practice.
+We assigned normal priors with a mean of 0 and a variance of 2.5 for the model coefficients, which helps to maintain reasonable uncertainty while avoiding overfitting.
+Additionally, an exponential prior was included to handle extra variation in the model, contributing to the stability of the estimated results.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define \( y_i \) as the predicted support percentage for Harris in the \( i \)-th poll.
+The predictor variables include \( x_1, x_2, x_3, x_4, x_5, x_6 \), corresponding to poll type (State or National), pollster identity (e.g., Marquette Law School, Siena/NYT), poll score, transparency score, state, and pollster organization respectively.
+The model can be described by the following equations:
 
 \begin{align}
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
+\mu_i &= \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_3 + \beta_4 x_4 + \beta_5 x_5 + \beta_6 x_6 \\
+\beta_0 &\sim \text{Normal}(0, 2.5) \\
+\beta_j &\sim \text{Normal}(0, 2.5), \quad j = 1, 2, 3, 4, 5, 6 \\
+\sigma &\sim \text{Exponential}(1)
 \end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+The model is executed in R using the \texttt{rstanarm} package.
+Default priors from \texttt{rstanarm} are used, with the priors set to have a mean of zero and a moderate standard deviation to ensure a reasonable level of regularization.
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+Considering the historical polling data and what we know about the political landscape, we believe that different aspects of polls will have a notable impact on Harris' predicted support in the upcoming election.
+Specifically, polls from McCourtney Institute/YouGov, YouGov/Center for Working Class Politics, higher poll scores, and greater transparency tend to have a positive influence on Harris' support.
+In contrast, polls from Siena/NYT, The Washington Post, YouGov, and YouGov Blue generally show a negative impact on her predicted support.
+Our purpose is to determine how much each polling characteristic affects voter support, thus helping us confirm or reconsider our assumptions about voter preferences.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+We used a Gaussian linear regression model to examine the connection between polling characteristics and Harris' predicted support percentage.
+The support percentage \( y_i \) is a continuous measure, and its distribution aligns well with the assumptions of Gaussian regression.
+This method allows us to investigate how several factors—like poll type, pollster score, and transparency level—affect the level of support for Harris.
+By numerically encoding these predictors, we can better understand the influences on polling outcomes, ultimately offering a clearer picture of Harris' potential performance in the upcoming election.
+```{r}
+#| label: tbl-summary-model
+#| tbl-cap: Summary of the Linear Regression Model
+#| echo: false
+#| warning: false
+
+first_model  <- readRDS(file = here::here("models/first_model.rds"))
+
+modelsummary(
+  list(
+    "first_model " = first_model 
+  )
+)
+```
+
+Further justification for this model is based on its ability to demonstrate how different polling organizations and their characteristics affect Harris' predicted support percentage.
+The intercept value represents the baseline level of support when all other predictors are set to zero, providing a reference point.
+Each coefficient then reflects the expected change in support, depending on factors like poll type, pollster identity, poll scores, and transparency measures.
+Positive coefficients, such as those for McCourtney Institute/YouGov and YouGov/Center for Working Class Politics, suggest increased support for Harris, while negative coefficients, such as those for Siena/NYT, The Washington Post, YouGov, and YouGov Blue, indicate a decrease in support.
+
+The relatively modest R^2 value reflects that the model only captures part of the variation in Harris' support, which is not unexpected given the unpredictable nature of polling data and the complex dynamics of voter behavior.
+Despite this, including key polling attributes allows us to examine how different factors contribute to voter support, helping us understand the sources of variation in predicted support levels.
+The choice of Gaussian linear regression is appropriate in this case, as it effectively models the continuous outcome variable and provides a clear framework for interpreting the relationship between polling features and voter preferences.
 

### 2024-10-24 scripts/06-model_data.R

@@ -18,7 +18,7 @@ analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 ### Model data ####
 first_model <-
   stan_glm(
-    formula = pct ~ pollster + pollscore + transparency_score,
+    formula = pct ~ poll_type + pollster + pollscore + transparency_score,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),

### 2024-10-26 scripts/03-clean_data.R
update cleaning data

@@ -8,17 +8,39 @@
 # Any other information needed? [...UPDATE THIS...]
 
 #### Workspace setup ####
+library(arrow)
 library(tidyverse)
 
 #### Clean data ####
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  filter(numeric_grade >= 3.0, candidate_name == "Kamala Harris") |>
-  select(poll_id, pollster, pollscore, transparency_score, display_name, state, pct) |>
-  mutate(poll_type = ifelse(is.na(state), "National", "State"))  # Add new column 'poll_type'
+legal_marijuana_states <- c(
+  "Colorado", "Washington", "Alaska", "Oregon", "Washington, D.C.", "California",
+  "Maine", "Massachusetts", "Nevada", "Michigan", "Vermont", "Guam", "Illinois", 
+  "Arizona", "Montana", "New Jersey", "New York", "Virginia", "New Mexico", 
+  "Connecticut", "Rhode Island", "Maryland", "Missouri", "Delaware", "Minnesota", "Ohio"
+)
+
+cleaned_data <- 
+  raw_data |> 
+  janitor::clean_names() |> 
+  filter(numeric_grade >= 2.7, candidate_name == "Donald Trump") |> 
+  mutate(end_date = mdy(end_date)) |>
+  filter(end_date >= as.Date("2024-07-15")) |>  # Trump announced joining campaign
+  mutate(
+    duration = as.numeric(difftime(end_date, min(end_date), units = "days")),  # New column: duration (end_date - start_date of Trump)
+    num_trump = round((pct / 100) * sample_size, 0),  # Number of respondents supporting Trump
+    methodology = ifelse(str_detect(methodology, "/"), "Mixed Voting", methodology),  # Replace "/" with "multiple ways of voting"
+    marijuana_legal = ifelse(state %in% legal_marijuana_states, 1, 0)  # Map whether the state allows marijuana legally
+  ) |> 
+  select(
+    poll_id, numeric_grade, methodology, transparency_score, 
+    end_date, sample_size, pollster_name = display_name,  # Rename display_name to pollster_name
+    state, pct, duration, num_trump, marijuana_legal
+  ) |> 
+  distinct() |> 
+  drop_na() # Omit rows with any NA values
 
 #### Save data ####
[…]

### 2024-10-26 scripts/03-clean_data.R
update test and train data

@@ -9,6 +9,7 @@
 
 #### Workspace setup ####
 library(arrow)
+library(rsample)
 library(tidyverse)
 
 #### Clean data ####
@@ -24,7 +25,7 @@ legal_marijuana_states <- c(
 cleaned_data <- 
   raw_data |> 
   janitor::clean_names() |> 
-  filter(numeric_grade >= 2.7, candidate_name == "Donald Trump") |> 
+  filter(numeric_grade >= 2.5, candidate_name == "Donald Trump") |> 
   mutate(end_date = mdy(end_date)) |>
   filter(end_date >= as.Date("2024-07-15")) |>  # Trump announced joining campaign
   mutate(
@@ -41,6 +42,15 @@ cleaned_data <-
   distinct() |> 
   drop_na() # Omit rows with any NA values
 
+# Perform a stratified split based on the 'state' variable to ensure all levels are present in both sets
+split <- initial_split(data = cleaned_data, prop = 0.7, strata = state)
+
+# Create training and testing sets
+analysis_data_train <- training(split)
+analysis_data_test <- testing(split)
+
 #### Save data ####
 write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")
 write_parquet(cleaned_data, "data/02-analysis_data/analysis_data.parquet")
+write_parquet(analysis_data_test, "data/02-analysis_data/test_data.parquet")
+write_parquet(analysis_data_train, "data/02-analysis_data/train_data.parquet")

### 2024-10-26 scripts/06-model_data.R
update model

@@ -11,23 +11,38 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(rsample)
+library(dplyr)
+
 
 #### Read data ####
 analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data_test <- read_parquet("data/02-analysis_data/test_data.parquet")
+analysis_data_train <- read_parquet("data/02-analysis_data/train_data.parquet")
 
 ### Model data ####
 first_model <-
   stan_glm(
-    formula = pct ~ poll_type + pollster + pollscore + transparency_score,
-    data = analysis_data,
+    formula = pct~ numeric_grade + as.factor(methodology) + duration + transparency_score+state
+    ,
+    data = analysis_data_train,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
-
 summary(first_model)
+
+vif(first_model)
+
+m2 <-lm(pct~ numeric_grade + as.factor(methodology) + duration +sample_size + transparency_score+ state,data=analysis_data_train)
+
+summary(m2)
+
+vif(m2)
+
+
 
 
 #### Save model ####

### 2024-10-26 scripts/06-model_data.R
fix formatting in model

@@ -13,6 +13,7 @@ library(tidyverse)
 library(rstanarm)
 library(rsample)
 library(dplyr)
+library(car)
 
 
 #### Read data ####
@@ -20,11 +21,11 @@ analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 analysis_data_test <- read_parquet("data/02-analysis_data/test_data.parquet")
 analysis_data_train <- read_parquet("data/02-analysis_data/train_data.parquet")
 
+
 ### Model data ####
 first_model <-
   stan_glm(
-    formula = pct~ numeric_grade + as.factor(methodology) + duration + transparency_score+state
-    ,
+    formula = pct~ numeric_grade + as.factor(methodology) + duration + transparency_score + state,
     data = analysis_data_train,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
@@ -33,20 +34,16 @@ first_model <-
     seed = 853
   )
 summary(first_model)
-
 vif(first_model)
 
-m2 <-lm(pct~ numeric_grade + as.factor(methodology) + duration +sample_size + transparency_score+ state,data=analysis_data_train)
-
-summary(m2)
-
-vif(m2)
-
-
+model2 <-lm(pct~ numeric_grade + as.factor(methodology) + duration + sample_size + transparency_score + state, 
+            data = analysis_data_train)
+summary(model2)
+vif(model2)
 
 
 #### Save model ####
 saveRDS(
-  first_model,
+  model2,
   file = "models/first_model.rds"
 )

### 2024-10-27 paper/paper.qmd
update appendix
update appendix A

@@
     "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
+  )
 )
@@
 # Appendix {-}
+
+# Pollster Methodology Overview and Evaluation
+## Overview of Siena/NYT
+Siena College Research Institute (SCRI) and The New York Times launched a collaborative political poll in July 2013.
+Siena/NYT  was known for its rigorous methodology and accuracy, which provided its first real-time midterm election poll in 2018.In 2024, FiveThirtyEight named it the most accurate pollster in the United States.
+The polling methodology emphasizes live phone interviews and representative sampling and focuses on transparency and statistical accuracy to provide a deep understanding of voter sentiment.
+
+## Target Population, Frame, and Sample
+* Target Population: Registered voters or likely voters in the United States, especially voters in major battleground states during an election in 2024.\
+* Sample Frame: U.S. registered voters based on a national voter file maintained by L2, with a cell phone number that matches the voter file.\
+* Sample Size: Sample sizes vary across different polls.
+The poll in late October 2024 surveyed over 2,500 voters, and 2,097 of them completed the full survey.
+The margin of error for likely voters is about ±2.2 percentage points.
+
+## Sample Recruitment
+The sample was conducted by live telephone interviews in both English and Spanish. Over 98% of respondents were contacted by telephone.
+
+## Sampling Approach and Trade-offs
+Siena/NYT used a stratified sampling method.
+Polls were stratified by demographic characteristics such as political party, race and region.
+This improves accuracy but adds cost and complexity.
+It also makes it challenging to reach certain populations such as young voters.\
+
+**Advantages of stratified sampling:**\
+* Generates a representative sample that captures the diverse opinions of different voter populations.\
+* Helps to ensure that under-represented groups are given appropriate weighting, and reduces potential bias.\
+* Provides a more accurate reflection of the wider population by stratifying on key characteristics.\
+
+**Disadvantages of stratified sampling:**\
+* Increased cost and time to complete polls, especially for live telephone interviews.\
+* There are challenges in reaching specific demographic groups, such as younger voters who may be less likely to participate in the poll.\
+* Reliance on weighting adjustments to correct for response discrepancies, which does not fully eliminate residual bias.
+
+## Non-response Handling
+Non-response was a key problem for Siena/NYT.
+The poll used weighted adjustments for demographic characteristics such as age, race, gender, education, and different political parties to address non-response bias.
+The weighting adjustment was used to ensure that the sample closely matches the larger population and compensates for differences in response rates across demographic groups.
+However, non-response can still present residual bias even with weighting, especially when certain demographic groups have been less likely to respond to survey calls.
+
+## Questionnaire Evaluation
+**Strengths:**\
+* Minimize bias through the use of straightforward and non-leading questions.\
+* Transparency was maintained by publishing the questions verbatim to allow for public scrutiny.\
+* Bilingual interviewers ensured that respondents could participate in their preferred language (English or Spanish), which increased the participation of Spanish-speaking voters and improved the quality of respondents' answers.\
+
+**Weaknesses:**\
+* The length of the poll can lead to respondent fatigue, which affects the quality of the data and increases dropout rates.\
+* It can be challenging to limit calls to less than 15 minutes, which can lead to incomplete or rushed responses, thus affecting the overall reliability of the data.\
+
+## Conclusion
+The Siena/NYT poll uses stratified sampling and live phone interviews to reach a representative sample of voters.
+While the use of composite weighting and bilingual interviews provides advantages such as transparency and reduced bias, challenges remain including high costs and the potential for bias due to non-response.
+Despite these drawbacks, Siena/NYT's commitment to transparency and rigorous methodology makes it a reliable source for understanding voter sentiment and opinion.
 

### 2024-10-27 paper/paper.qmd
update Appendix A and Part of Appendix B

@@
 **Advantages of stratified sampling:**\
+
 * Generates a representative sample that captures the diverse opinions of different voter populations.\
@@
 **Disadvantages of stratified sampling:**\
+
 * Increased cost and time to complete polls, especially for live telephone interviews.\
@@
 **Strengths:**\
+
 * Minimize bias through the use of straightforward and non-leading questions.\
@@
 **Weaknesses:**\
+
 * The length of the poll can lead to respondent fatigue, which affects the quality of the data and increases dropout rates.\
@@
 While the use of composite weighting and bilingual interviews provides advantages such as transparency and reduced bias, challenges remain including high costs and the potential for bias due to non-response.
-Despite these drawbacks, Siena/NYT's commitment to transparency and rigorous methodology makes it a reliable source for understanding voter sentiment and opinion.
+Despite these drawbacks, Siena/NYT's commitment to transparency and rigorous methodology makes it a reliable source for understanding voter sentiment and opinion.\
+
+# Idealized Methodology and Survey
+## Overview
+The objective of this survey is to predict voter sentiment in the upcoming U.S.
+presidential election, by using a budget of $100,000 to collect accurate and varied data on voting intentions, candidate favourability, and key issues from a representative sample of registered or likely voters across the United States.
+The methodology is designed to maximize accuracy, minimize bias and take into account a variety of demographic, geographic and political factors that influence voting behaviour.
+
+## Sampling Approach
+The sampling approach is designed to increase coverage and ensure that a representative voting population is covered.
+This will be achieved by using a combination of stratified random sampling and quota sampling of key demographics.
+
+### Stratification Variables 
+* Age: 18-29, 30-44, 45-64, 65+\
+* Gender: Male and Female\
+* Race: White, Black /African American, Hispanic/Latino, Asian, Native and Other\
+* Education level: High School, Some College, Bachelor's Degree, Graduate Degree, Other\
+* Geographic region: Northeast, Midwest, South, West\
+* Political Party: Democratic, Republican, Independent, Other\
+
+### Sample Size
+The target sample size was 10,000 respondents, which are stratified by the Stratification Variables described above.
+This stratification ensures that all major voter groups are proportionately represented.
+10,000 samples have a margin of error of about ±1% and a confidence level of 95%, which is appropriate for predicting elections.
+
+## Recruitment Strategy
+The recruitment strategy was separated into two main approaches to ensure a diverse and representative sample:
+
+**Online Survey panels:**\
+
+* Work with established survey panels such as Lucid or YouGov.\
+* These panels have access to large representative databases of voters.\
+* Recruiting through panels ensures quality and reliability, as they have built-in validation and quality control processes.\
+
+**Social Media Advertising:**\
+
+* Use social media platforms such as Facebook, Instagram and LinkedIn to reach potential respondents.\
+* Target groups that are underrepresented in traditional panels, including young voters and minority groups.\
+* Social media ads will be customized with demographic information to increase reach and participation.\
+
+**Incentives:** Offer gift card lottery prizes to all participants to encourage participation and ensure a high response rate.
+
+## Data validation and quality control
+To maintain the integrity of the data, we will take the following measures:\
+
+* **Attention Checks:** At least two ‘attention check’ questions will be included in the survey to identify inattention or robots.\
+* **Duplicate Detection:** Use email or IP-based verification to prevent duplicate responses. Ensure that each respondent provides only one response set to keep the dataset unique.\
+* **Response Time Monitoring:** Track the time it takes respondents to complete surveys. Responses with apparently faster-than-average completion times are labelled as potentially low-quality.\
+* **Data Consistency Check:** Analyses the consistency of responses, especially between related questions. Inconsistent answers will be labelled for review.\
+* **Panel partner validation:** For respondents recruited through an online survey panel, rely on the panel provider's in-built validation systems.
+These systems use various quality checks, such as identity verification and response consistency, which ensure high-quality data from panel participants.
+
+## Poll aggregation and forecasting
+### Poll aggregation
 

### 2024-10-27 paper/paper.qmd
update Appendix B

@@
 ### Poll aggregation
+* ‘Poll of polls’ approach: Survey data will be combined with data from some reliable polling sources such as Lucid, YouGov and others.
+This approach aggregates the results of multiple reputable polls to improve the forecast reliability by reducing bias and individual polling errors.\
+* Weighting adjustments: Polls are weighted according to sample quality, size, repeatability, and demographic match.
+Demographic mismatches are adjusted using raking to ensure that the aggregated data accurately represents the U.S.
+population.
+
+### Forecasting Method
+* Bayesian modelling: Aggregate polling data is combined with historical electoral trends and demographic information using Bayesian statistical models.
+This approach allows for dynamic updating as new data becomes available, which improves accuracy.
+\
+* Uncertainty Quantification: Includes confidence intervals to express uncertainty in forecasts for a more detailed interpretation.
+
+## Budget Allocation
+* Survey Panel Recruitment: $50,000\
+* Social Media Advertising: $50,000\
+* Incentives(lottery prizes): $15,000\ 
+* Data Cleaning and Validation: $5,000\
+* Poll Aggregation and Modeling: $10,000
+
+## Survey Implementation
+The survey will be available via Google Forms to ensure broad accessibility and easy data collection.
+The link to the survey will be distributed via email invitations to panellists and targeted social media adverts.
+To ensure maximum reach and diversity, multiple channels will be used, including Facebook, Instagram, and other social media platforms.\
+
+**Distribution Plan:**\
+
+* **Panel invitations:** Members of established survey panels (e.g. Lucid, YouGov) will receive email invitations to participate in the survey.\
+* **Social media activities:** Targeted adverts will be placed on social media platforms to reach under-represented groups, especially young voters and national minority groups.\
+* **Follow-up reminders:** An automated reminder email will be sent to participants who have not completed the survey to maximize response rates.\
+* **Survey Monitoring:** Response rates will be closely monitored throughout the data collection period and sampling methods will be adjusted if certain population quotas are not reached.\
+* **Accessibility:** The survey will be mobile-friendly, which will allow respondents to complete the survey on any device.
+
+## Survey Structure
 

### 2024-10-27 paper/paper.qmd
update data section

@@
 library(tidyverse)
-library(palmerpenguins)
+library(dplyr)
+library(here)
+library(ggplot2)
+library(kableExtra)
 library(modelsummary)
+library(rstanarm)
 ```
@@
 
-We use the statistical programming language R [@citeR] to process and analyze polling data for the 2024 US Presidential election.
-The data, obtained from a repository of publicly available polls, includes variables from numerous pollsters across the country [@citedata].
-The aim is to create a reproducible forecast model by focusing on high-quality polls and narrowing our scope to Kamala Harris as a candidate of interest.
-Following methodologies discussed by "Telling Stories with Data" [@tellingstories], we examine how polling data reflects electoral behavior and voter preferences.
+We use the statistical programming language R [@citeR] to process and analyze polling data for the 2024 U.S.
+Presidential election.
+The dataset used for this analysis was obtained from the FiveThirtyEight 2024 U.S.
+Presidential Election Polls [@citedata].
+It consists of polling data for the 2024 general election, covering various polling organizations and methodologies.
+Following methodologies discussed by "Telling Stories with Data" [@tellingstories], we forecast election outcomes using the "poll of polls" method, which aggregates results from multiple polls to reduce bias and provide a more accurate representation of voter sentiment.
 
 The dataset includes 15,891 rows and 52 columns, covering various pollster attributes such as pollster name, state, methodology, and polling results.
-We filter the dataset to include only high-quality polls, i.e., those with a numeric grade of 3.0 or higher, ensuring that only reputable and well-documented pollster results are used in our model.
-Additionally, we focus solely on polls that include Kamala Harris as a candidate, which helps narrow our analysis to a specific electoral scenario.
+To ensure the reliability of our analysis, we filter the data to include only polls with a numeric grade of 2.5 or higher, which represents high-quality, reputable pollsters.
+This filtering allows us to focus on polls that follow rigorous standards and have demonstrated transparency and accuracy.
+
+Additionally, we limit the dataset to polls conducted after July 15, 2024, when Donald Trump officially announced his campaign, ensuring that the data reflects the most current public sentiment.
+Other similar datasets from prior elections, such as data from previous general election cycles, could have been used for comparison.
+However, given that this analysis focuses on the upcoming 2024 election and the shift in public opinion, the most relevant data is specific to the current cycle.
 
@@
 
-Polling data captures voter preferences and electoral forecasts by collecting responses from a representative sample of the population.
-In this case, pollsters attempt to gauge public opinion by surveying individuals on their preferred candidate, adjusting for demographic factors and political trends.
-The raw data entries reflect the outcomes of these surveys.
+Polling data is a measurement of public sentiment captured through various survey methods.
+Polling organizations collect responses from individuals representing different segments of the population and ask them about their voting preferences.
+These responses are then weighted to reflect a more accurate representation of the electorate, based on factors like age, gender, race, and geographic region.
 
-Pollsters often rely on random sampling methods to recruit participants, as discussed in [@ todo], ensuring a diverse and representative group.
-Some pollsters use online platforms, while others use phone interviews or in-person surveys.
-The dataset captures these variations through variables such as `methodology` and `sample_size`.
-Sampling errors, response biases, and adjustments (e.g., weighting respondents based on age, race, or geographic region) are part of how this world phenomenon is translated into data entries.
+For this dataset, the poll results reflect the percentage of respondents who support a particular candidate.
+Different polling methods—such as live phone interviews, online panels, and mixed methodologies—capture this information.
+Each polling organization applies its own methodology, which can influence the results.
+For example, polls that use live interviews may experience different respondent behavior than those that use online surveys.
+More details on polling methodologies can be found in the [ABC News methodology explanation](https://abcnews.go.com/538/trump-leads-swing-state-polls-tied-biden-nationally/story?id=109506070).
 
-The process begins with identifying the population of interest—likely voters or registered voters—and applying statistical adjustments to the raw responses.
-Pollsters handle non-response through weighting or imputation methods, ensuring that missing data or low response rates do not skew the results significantly.
-The column `numeric_grade` reflects how well these pollsters adhere to rigorous methodology, allowing us to filter for only the most reliable sources in our analysis.
+The key measurement process involves converting real-world voter preferences into a dataset of percentages that reflect support for a candidate at a specific point in time.
+Polling organizations typically provide this data at a state or national level, which allows for both localized and broad interpretations of voter sentiment.
 
@@
 
-### Percent Support (pct)
-The primary outcome variable in this dataset is the percentage of respondents who support a given candidate.
-This is represented by the pct variable, which is reported by pollsters for each candidate they survey.
-For Kamala Harris, this percentage reflects her standing in polls, and variations in this metric can indicate shifts in voter preference over time.
-
-Below is a summary table showing the average, minimum, and maximum percent support for Kamala Harris across high-quality polls:
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+### Percent Support for Donald Trump (pct)
+The primary outcome variable is the percentage (`pct`) of respondents who indicated support for Donald Trump in the 2024 general election.
+This percentage is calculated based on the total number of respondents in each poll divide by `sample_size`.
+The data includes observations from various states, providing both national and state-specific measures of Trump’s support.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-trump-pct
+#| fig-cap: "Donald Trump's polling percentages from July to October 2024.
+Each dot indicates the polling percentage for Trump on a specific date, while the blue line shows the trend in Trump's support."
 #| echo: false
+#| warning: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+cleaned_data <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))
+
+cleaned_data <- cleaned_data %>%
+  mutate(end_date = as.Date(end_date))  # Convert to Date format if not already
+
+ggplot(cleaned_data, aes(x = end_date, y = pct)) +
+  geom_point() +  # Add points for individual poll data
+  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") +  # Show month and year, with one label per month
+  labs(
+    x = "Date of Poll",
+    y = "Polling Percentage (%)",
+  ) +
+  theme_minimal() +  # Use a clean minimal theme
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14),  # Center and adjust title size
+    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for readability
+  ) +
+  geom_smooth()
 ```
 
-Talk more about it.
+@fig-trump-pct shows Donald Trump's polling percentages over time from July to October 2024.
+Each black dot represents an individual poll conducted on a specific date, indicating the percentage of voters who supported Trump in that poll.
+The blue line represents a trendline, smoothing out the individual poll results to show the general trajectory of Trump's support over time.
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+Initially, Trump's polling percentage appears stable with small fluctuations around 45%.
+However, as the campaign progresses into October, there is a slight upward trend in Trump's polling percentage, suggesting that his support increased as the election neared.
 
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-```
-
-Talk way more about it.
+The shaded region around the blue line represents the confidence interval, indicating the range within which the true polling percentage is likely to fall, accounting for sampling variation.
 
@@
 
-### Pollster Name (display_name)
-This variable represents the pollster responsible for each entry in the dataset.
-Different pollsters may use varying methods and possess differing levels of reliability, which the numeric_grade helps quantify.
-High-quality pollsters (numeric_grade ≥ 3.0) are emphasized in this analysis to ensure the robustness of the forecast.
+### Polling Methodology (methodology)
+The `methodology` variable describes the method each pollster used to collect data.
+It includes approaches such as live phone interviews, online surveys, and mixed methods.
+For polls that used multiple collection methods (e.g., phone and online), we labeled them as "Mixed Voting" for simplicity.
+The methodology is important because different approaches can introduce varying degrees of bias, influencing the final reported percentages.
 
-### Internal Polling (internal)
-The variable internal is a binary indicator that identifies whether a poll was commissioned by a political campaign or interest group.
-Internal polls can sometimes be biased, either in how respondents are selected or how results are reported.
-However, the filtering for high-quality pollsters ensures that even internal polls meet certain standards of rigor.
+Placeholder for a table showing the distribution of polling methodologies across different states.
 
-### Partisan Polling (partisan)
-Like internal polling, partisan polling can introduce bias, as it may be sponsored by organizations with a vested interest in the election outcome.
-The partisan variable, similar to the internal variable, flags such polls.
-In the dataset, these are rare but still important to identify, especially when making impartial predictions.
+### State (state)
+The `state` variable identifies whether the poll is state-specific or national.
+In state-specific polls, the data reflects localized voter preferences, while national polls aggregate opinions across the entire country.
+For this analysis, we ignore national polls and focus entirely on state polls because electoral outcomes are determined on a state-by-state basis in the U.S.
+election system.
 
-### Party Affiliation (party)
-The party variable indicates the political party that the poll respondent supports.
-This is key to understanding the partisan leanings of the sample.
-For Kamala Harris, her affiliation with the Democratic Party is represented in this column.
+### Polling Score and Transparency (numeric_grade and transparency_score)
+The `numeric_grade` variable is a rating assigned to each polling organization, indicating the reliability of the poll.
+Pollsters with higher numeric grades are considered more reliable and consistent in their methodology (e.g.
+higher than 2.5).
+Additionally, the `transparency_score` measures how openly a pollster shares their methodology and data, which further affects the trustworthiness of their results.
 
-Below is a table summarizing the distribution of party affiliations in polls that include Kamala Harris:
+### Sample Size (sample_size)
+The `sample_size` variable represents the total number of respondents surveyed in each poll.
+A larger sample size generally leads to more reliable and precise estimates of voter sentiment, as it reduces the margin of error.
+In contrast, smaller sample sizes can result in greater variability and less confidence in the results.
 
-### Race ID (race_id)
-This variable identifies the electoral race or contest being polled.
-In this analysis, the focus is on the 2024 presidential election.
-Tracking results across different races (i.e., primary versus general election) helps in understanding shifts in voter opinion throughout the campaign.
+### Poll Duration (duration)
+The `duration` variable is a constructed variable that represents how long Donald Trump has been in the 2024 presidential campaign, measured as the number of days from his official campaign announcement on July 15, 2024 until the `end_date` of each poll.
+This variable helps quantify how much time has passed since Trump officially entered the race and allows us to examine how his support has evolved over the course of his campaign.
 

### 2024-10-27 paper/paper.qmd
Update Appendix B: Survey Structure

@@
 ## Survey Structure
+**Survey Introduction:**\
+Welcome!
+We are surveying to better understand voter preferences and priorities for the upcoming U.S.
+presidential election.
+Your participation is important and your answers will help us accurately predict the outcome of the election.
+It will take approximately 10 minutes to complete the survey.
+All responses are confidential and will be used for research purposes only.\
+If you have any questions or concerns, please feel free to contact our research team at winniekeai23@gmail.com (Ziyuan Shen, Leo Liu, Dezhen Chen).\
+As a thank you for your participation, you will be entered into a raffle to win a grand prize of a gift card.
+We are deeply grateful for your participation and appreciate the time and effort that you put in.\
+
+**Survey Question:**\
+
+**Part 1: Screening for eligibility**\
+1.Are you an eligible U.S. citizen?\
+* Yes / No\
+2.Are you currently 18 years of age or older?\
+* Yes / No
+3.Have you completed your registration to become a voter?\
+* Yes / No / Plan to register\
+
+**Part 2: Demographics**\
+
+4.What is your age?\
+* 18-24 / 25-34 / 35-44 / 45-54 / 55+\
+5.What is your gender?\
+* Male / Female / Non-binary / Prefer not to say\
+6.Which of the following best describes your education level?\
+* High School / Some College / Bachelor's Degree / Graduate Degree / Other\
+7.Which region of the U.S. do you currently reside in?\
+* Northeast / Midwest / South / West\    
+8.Do you generally identify with a political party?\
+* Democratic / Republican / Independent / None\
+
+**Part 3: Voting Intentions**\
+
+9.How likely are you to participate in the upcoming presidential election?\
+* Very Likely / Somewhat Likely / Not Sure / Unlikely / Very Unlikely\
+10.If the presidential election were held today, for which candidate would you vote?\
+* Kamala Harris (Democrat) / Donald Trump (Republican) / Undecided / Prefer not to say\
+11.What are the top three issues that will influence your vote?\
+* Economy / Healthcare / Education / Gun Policy / Taxes / Foreign Policy / Social Security / Civil Rights / Technology / Privacy / Other[text]\
+
+**Part 4: Information Sources and Engagement**\
+
+12.Which of the following sources do you rely on most for political news and information?\
+* Television News / Newspapers / Online News Websites / Social Media / Radio / Friends and Family / Other\
+13.How often do you engage in discussions about political topics with friends or family?\
+* Daily / Weekly / Monthly / Rarely / Never\
+
+**Part 5: Verify**\
+
+14.Please select 'Agree' to verify that you are paying attention.\
+* Agree / Disagree\
+15.Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.\
+* Yes / No\
+
+**End Part:**\
+Thank you for your participation!\
+Your responses are valuable to us in anticipating the upcoming election and understanding voters' priorities.
+If you have any questions or would like more information about our research, please feel free to contact us at winniekeai23@gmail.com (Ziyuan Shen, Leo Liu, Dezhen Chen).
 

### 2024-10-27 paper/paper.qmd
update survey email

@@
 All responses are confidential and will be used for research purposes only.\
-If you have any questions or concerns, please feel free to contact our research team at winniekeai23@gmail.com (Ziyuan Shen, Leo Liu, Dezhen Chen).\
+If you have any questions or concerns, please feel free to contact our research team at [winniekeai23@gmail.com](mailto:winniekeai23@gmail.com) (Ziyuan Shen, Leo Liu, Dezhen Chen).\
 As a thank you for your participation, you will be entered into a raffle to win a grand prize of a gift card.
@@
 Your responses are valuable to us in anticipating the upcoming election and understanding voters' priorities.
-If you have any questions or would like more information about our research, please feel free to contact us at winniekeai23@gmail.com (Ziyuan Shen, Leo Liu, Dezhen Chen).
+If you have any questions or would like more information about our research, please feel free to contact us at [winniekeai23@gmail.com](mailto:winniekeai23@gmail.com)(Ziyuan Shen, Leo Liu, Dezhen Chen).
 

### 2024-10-28 paper/paper.qmd
update survey

@@
 The link to the survey will be distributed via email invitations to panellists and targeted social media adverts.
-To ensure maximum reach and diversity, multiple channels will be used, including Facebook, Instagram, and other social media platforms.\
+To ensure maximum reach and diversity, multiple channels will be used, including Facebook, Instagram, and other social media platforms.
+The link to the survey is [here](https://forms.gle/y4Xh2oQ544DYcCXWA).\
 

### 2024-10-28 paper/paper.qmd
update abstract

@@
 date-format: long
-abstract: "In this paper, we use a logistic regression model based on \"poll-of-polls\" data to predict the winner of the 2024 U.S.
-presidential election.
-By combining multiple polls, the model smooths out short-term fluctuations in surveys to make more reliable estimates of voter preferences.
-The findings show early trends in the leading candidates and reflect public opinion and its evolution through the election period.
-This prediction improves understanding of electoral trends and helps to explain the changing political scene more clearly."
+abstract: "In this paper, we built a linear regression model based on \"poll-of-polls\" data to predict the winner of the 2024 U.S.
+By combining data from multiple polls, our model can predict voter preferences more consistently and predict that Donald Trump is likely to win.
+This approach helps reduce the short-term variation present in individual polls and provides a clearer view of long-term electoral trends.
+Our findings contribute to understanding the dynamics of public opinion during election campaigns, which helps the public and political strategists make more informative decisions."
 format: pdf

### 2024-10-28 paper/paper.qmd
update paper

@@
 library(rstanarm)
+library(modelsummary)
 ```
@@
 # Model {#sec-model}
-Our modeling approach aims to quantify the relationship between polling characteristics and the probability of Harris winning the election.
-We use a generalized linear model (GLM) to evaluate how different factors—such as poll type, polling organization, poll score, and transparency score—impact Harris' support rate.
-The model is implemented using the stan_glm function, with a Gaussian distribution applied to describe the variability in support percentages.
+Our modeling approach aims to quantify the relationship between various polling metrics and the percentage support for a candidate.
+For this analysis, we use a linear model (LM) to examine how factors such as poll grade, methodology, poll duration, sample size, transparency score, and state influence support percentages.
+The model is implemented using the lm function, with a Gaussian distribution to capture the variability in support rates.
 
-In our analysis, we filtered the data to include only polls from organizations with a poll score above 3, ensuring the reliability of our data sources.
-We selected predictors including  poll_type, pollster, pollscore, and transparency_score.
-Since the response variable (support percentage) is continuous, we utilized a Gaussian linear regression model.
+In this analysis, we use predictors that reflect both the methodological quality and structural characteristics of each poll.
+Specifically, we include variables such as numeric_grade, which quantifies the poll’s quality, methodology, duration (the length of the election period), sample_size, transparency_score, and state (the regional factor).
+This selection of predictors ensures a comprehensive view of the factors impacting support percentage.
 
-The model assumes that the distribution of support percentage, given the polling characteristics, follows a normal distribution.
-This assumption makes the parameter estimation more straightforward and is commonly used in practice.
-We assigned normal priors with a mean of 0 and a variance of 2.5 for the model coefficients, which helps to maintain reasonable uncertainty while avoiding overfitting.
-Additionally, an exponential prior was included to handle extra variation in the model, contributing to the stability of the estimated results.
+The model assumes that the distribution of support percentage, given these polling characteristics, follows a normal distribution.
+This Gaussian assumption facilitates parameter estimation, which is a standard approach in linear regression.
+To prevent overfitting and ensure interpretability, we assume moderate priors, maintaining balanced uncertainty across our predictors.
+This approach enables us to assess the impact of polling characteristics on candidate support while ensuring stability and robustness in our findings.
 
 ## Model set-up
+The model now predicts Trump's support percentage using the following predictor variables:
 
-Define \( y_i \) as the predicted support percentage for Harris in the \( i \)-th poll.
-The predictor variables include \( x_1, x_2, x_3, x_4, x_5, x_6 \), corresponding to poll type (State or National), pollster identity (e.g., Marquette Law School, Siena/NYT), poll score, transparency score, state, and pollster organization respectively.
-The model can be described by the following equations:
+Numeric Grade (numeric_grade): Represents the quality rating of the poll.
+
+Methodology (methodology): Different methods used to conduct the poll, such as live phone, mixed voting, or online ads.
+
+Poll Duration (duration): The the length of the election period was conducted.
+
+Sample Size (sample_size): The number of respondents in the poll.
+
+Transparency Score (transparency_score): A measure of how transparent the polling data and methodology are.
+
+State (state): A categorical variable representing the U.S. state where the poll was conducted.
+
+The model takes the form:
 
 \begin{align}
-y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
-\mu_i &= \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_3 + \beta_4 x_4 + \beta_5 x_5 + \beta_6 x_6 \\
-\beta_0 &\sim \text{Normal}(0, 2.5) \\
-\beta_j &\sim \text{Normal}(0, 2.5), \quad j = 1, 2, 3, 4, 5, 6 \\
-\sigma &\sim \text{Exponential}(1)
+y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \
+\mu_i &= \beta_0 + \beta_1 \cdot numeric_grade_i + \beta_2 \cdot methodology_i + \beta_3 \cdot duration_i + \beta_4 \cdot sample_size_i + \beta_5 \cdot transparency_score_i + \beta_6 \cdot state_i + \epsilon_i \
+\epsilon_i &\sim \text{Normal}(0, \sigma^2)
 \end{align}
+
+Where:
+Where: 
+\begin{align}
+\beta_0 & \text{ is the intercept term} \\
+\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6 & \text{ are the coefficients for each predictor} \\
+\sigma^2 & \text{ is the variance of the error term}
+\end{align}
+
 The model is executed in R using the \texttt{rstanarm} package.
@@
 ### Model justification
+Existing research and political science theories suggest that factors such as poll quality, sample size, transparency, methodology, poll duration, and the state where the poll takes place can significantly influence Trump's support percentage.
+Higher quality polls and larger sample sizes are believed to yield more reliable estimates, while transparency scores can affect levels of public trust, potentially altering support.
+Moreover, different polling methodologies (e.g., online surveys, telephone interviews) may affect how representative the sample is, while longer polling durations can reflect shifts in public sentiment over time.
+State-specific factors, such as local political events or population characteristics, can also contribute to the variation in support.
+The timing of the poll, particularly in relation to key political events, might further influence public opinion.
 
-Considering the historical polling data and what we know about the political landscape, we believe that different aspects of polls will have a notable impact on Harris' predicted support in the upcoming election.
-Specifically, polls from McCourtney Institute/YouGov, YouGov/Center for Working Class Politics, higher poll scores, and greater transparency tend to have a positive influence on Harris' support.
-In contrast, polls from Siena/NYT, The Washington Post, YouGov, and YouGov Blue generally show a negative impact on her predicted support.
-Our purpose is to determine how much each polling characteristic affects voter support, thus helping us confirm or reconsider our assumptions about voter preferences.
-
-We used a Gaussian linear regression model to examine the connection between polling characteristics and Harris' predicted support percentage.
-The support percentage \( y_i \) is a continuous measure, and its distribution aligns well with the assumptions of Gaussian regression.
-This method allows us to investigate how several factors—like poll type, pollster score, and transparency level—affect the level of support for Harris.
-By numerically encoding these predictors, we can better understand the influences on polling outcomes, ultimately offering a clearer picture of Harris' potential performance in the upcoming election.
+A linear regression model was chosen to predict Trump's support percentage because the dependent variable is continuous and tends to follow a normal distribution.
+Linear regression is a straightforward method to analyze how multiple factors contribute to an outcome, and it offers easy-to-interpret coefficients for each predictor.
+The model helps us determine the extent to which different aspects of polling influence the level of public support for Trump.
 ```{r}
@@
 
-first_model  <- readRDS(file = here::here("models/first_model.rds"))
+linear_model <- readRDS(file = here::here("models/first_model.rds"))
 
@@
   list(
-    "first_model " = first_model 
-  )
+    "Linear Model" = linear_model
+  ),
+  statistic = NULL  # 这将不显示标准误
 )
@@
 
-Further justification for this model is based on its ability to demonstrate how different polling organizations and their characteristics affect Harris' predicted support percentage.
-The intercept value represents the baseline level of support when all other predictors are set to zero, providing a reference point.
-Each coefficient then reflects the expected change in support, depending on factors like poll type, pollster identity, poll scores, and transparency measures.
-Positive coefficients, such as those for McCourtney Institute/YouGov and YouGov/Center for Working Class Politics, suggest increased support for Harris, while negative coefficients, such as those for Siena/NYT, The Washington Post, YouGov, and YouGov Blue, indicate a decrease in support.
-
-The relatively modest R^2 value reflects that the model only captures part of the variation in Harris' support, which is not unexpected given the unpredictable nature of polling data and the complex dynamics of voter behavior.
-Despite this, including key polling attributes allows us to examine how different factors contribute to voter support, helping us understand the sources of variation in predicted support levels.
-The choice of Gaussian linear regression is appropriate in this case, as it effectively models the continuous outcome variable and provides a clear framework for interpreting the relationship between polling features and voter preferences.
+Further justification for using this model comes from its alignment with the central limit theorem, which suggests that with sufficient sample size, the distribution of poll percentages should approximate normality.
+Additionally, the relationships between the predictors (e.g., poll quality, methodology type) and support align well with established theories in political behavior, giving a solid theoretical underpinning to our model.
+The simplicity of a linear regression approach also helps mitigate overfitting, ensuring our results are generalizable to a broader set of polling data.
+The model assumptions, including linearity, independence, and normality of residuals, are adequately satisfied by our dataset, making this approach not only convenient but also statistically robust for our analysis.
 
 # Results {#sec-result}
+## Model Results and Interpretation
+The linear regression model, using 384 data points, estimated the factors influencing Trump's support levels.
+The intercept, estimated at 43.39, represents the level of support when all other predictors are at baseline.The model achieved an R-squared value of 0.85, indicating that 85% of the variance in Trump's support percentage can be explained by the predictors included in the model.
+The adjusted R-squared value of 0.82 also shows that the model effectively captures the relationships between variables without overfitting.The Root Mean Square Error (RMSE) was 2.03, indicating the average difference between predicted and actual values.
+The relatively low RMSE value suggests that the model provides reasonably accurate predictions.The results highlight that numeric_grade and sample_size are particularly important in predicting support levels, with larger and higher-quality polls offering more reliable estimates.
+The transparency score and state-level coefficients further provide insight into regional differences and the role of trust in polling, helping us better understand the dynamics behind Trump's public support.The coefficients for numeric_grade and sample_size underline the importance of poll quality and sample size in predicting support levels.
+Larger, higher-quality polls offer more robust estimates.
+Additionally, transparency and state effects provide insight into regional differences and trust factors affecting polling results, giving a clearer understanding of the dynamics influencing Trump's public support.
 
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```

### 2024-10-28 paper/paper.qmd
update paper

@@
 ## Predictor variables
-
-### Polling Methodology (methodology)
+Polling Methodology (methodology)
 The `methodology` variable describes the method each pollster used to collect data.
@@
 
-### State (state)
+ State (state)
 The `state` variable identifies whether the poll is state-specific or national.
@@
 
-### Polling Score and Transparency (numeric_grade and transparency_score)
+Polling Score and Transparency (numeric_grade and transparency_score)
 The `numeric_grade` variable is a rating assigned to each polling organization, indicating the reliability of the poll.
@@
 
-### Sample Size (sample_size)
+ Sample Size (sample_size)
 The `sample_size` variable represents the total number of respondents surveyed in each poll.
@@
 
-### Poll Duration (duration)
+ Poll Duration (duration)
 The `duration` variable is a constructed variable that represents how long Donald Trump has been in the 2024 presidential campaign, measured as the number of days from his official campaign announcement on July 15, 2024 until the `end_date` of each poll.
@@
   ),
-  statistic = NULL  # 这将不显示标准误
+  statistic = NULL 
 )

### 2024-10-28 paper/paper.qmd
update paper

@@
 
-\begin{align}
-y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \
-\mu_i &= \beta_0 + \beta_1 \cdot numeric_grade_i + \beta_2 \cdot methodology_i + \beta_3 \cdot duration_i + \beta_4 \cdot sample_size_i + \beta_5 \cdot transparency_score_i + \beta_6 \cdot state_i + \epsilon_i \
+\begin{align*}
+    y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
+    \mu_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{methodology}_i \\
+          &\quad + \beta_3 \cdot \text{duration}_i + \beta_4 \cdot \text{sample\_size}_i \\
+          &\quad + \beta_5 \cdot \text{transparency\_score}_i + \beta_6 \cdot \text{state}_i + \epsilon_i \\
     \epsilon_i &\sim \text{Normal}(0, \sigma^2)
-\end{align}
+\end{align*}
 
-Where:
-Where: 
-\begin{align}
-\beta_0 & \text{ is the intercept term} \\
-\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6 & \text{ are the coefficients for each predictor} \\
-\sigma^2 & \text{ is the variance of the error term}
-\end{align}
+\textbf{Where:}
+\begin{itemize}
+    \item $\beta_0$ is the intercept term.
+    \item $\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6$ are the coefficients for each predictor.
+    \item $\sigma^2$ is the variance of the error term.
+\end{itemize}
 
@@
 Our results are summarized in @tbl-modelresults.
-
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  )
-)
-```
 

### 2024-10-29 paper/paper.qmd
update paper model

@@
 library(modelsummary)
+library(arrow)
+library(knitr)
+library(kableExtra)
+library(usmap)
+
 ```
@@
 
-linear_model <- readRDS(file = here::here("models/first_model.rds"))
+model2 <- readRDS(file = here::here("models/first_model.rds"))
 
@@
   list(
-    "Linear Model" = linear_model
+    "Linear Model" = model2
   ),
@@
 Additionally, transparency and state effects provide insight into regional differences and trust factors affecting polling results, giving a clearer understanding of the dynamics influencing Trump's public support.
+
+## Predicted Electoral Outcomes
+We employed a regression model to estimate the percentage of votes Trump is likely to receive in each state.
+Using these predicted results and the electoral vote allocations, we identified the winner for each state and calculated the total electoral votes for both Trump and Harris.
+
+The following table（@predictiontable） presents a summary of the predictions, including Trump’s estimated percentage, the number of electoral votes in each state, and the projected winner.
+For instance:
+
+ • In Arizona, Trump is expected to receive 48.94% of the vote, resulting in a win for Harris with 11 electoral votes.
+ • In Missouri, Trump is projected to receive 51.64%, thereby winning all 10 electoral votes for that state.
+ • In Ohio, with an estimated 51.98% of the vote, Trump secures Ohio’s 18 electoral votes.
+
+Electoral Vote Count: Trump Electoral Votes: 98 - Harris Electoral Votes: 239.
+This indicates that Harris is projected to win the 2024 U.S.
+Presidential Election with 239 electoral votes, while Trump is projected to gather 98.
+These results hinge on the outcomes in various battleground states, with several being extremely close.
+```{r predictiontable}
+#| echno: false
+#| label: predictiontable
+#| tbl-cap: Prediction for Trump and Harris by Electoral College
+#| echo: false
+#| warning: false
+#| message: false
+
+# Load test data
+analysis_data_test <- read_parquet(here::here("data/02-analysis_data/test_data.parquet"))
+analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
+
+# Get the unique state names from training and test data
+unique_states_train <- unique(analysis_data_train$state)
+unique_states_test <- unique(analysis_data_test$state)
+
+# Find common states between training and test data and filter test data to only keep these states
+common_states <- intersect(unique_states_train, unique_states_test)
+analysis_data_test <- analysis_data_test %>%
+  filter(state %in% common_states)
+
+# Define the number of electoral votes for each state
+electoral_votes <- data.frame(
+  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida",
+            "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", 
+            "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
+            "Missouri", "Montana", "Nebraska", "Nevada", 
+            "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", 
+            "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", 
+            "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", 
+            "District of Columbia"),
+  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
+                      3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3))
+# Convert methodology column to character type for recoding
+analysis_data_test$methodology <- as.character(analysis_data_test$methodology)
+
+# Recode the 'Email' level in the methodology column to 'Online Panel'
+analysis_data_test$methodology[analysis_data_test$methodology == "Email"] <- "Online Panel"
+
+# Use the trained regression model to predict Trump's support percentage in each state
+analysis_data_test$predicted_percent_trump <- predict(model2, newdata = analysis_data_test)
+analysis_data_test$predicted_percent_trump
+total_trump <- aggregate(predicted_percent_trump ~ state, data = analysis_data_test, FUN = mean)
+
+# Determine the winner in each state based on Trump's predicted percentage
+state_predictions <- merge(total_trump, electoral_votes, by = "state")
+
+# Determine the winner in each state based on Trump's predicted percentage
+state_predictions$winner <- ifelse(state_predictions$predicted_percent_trump > 50, "Trump", "Harris")
+
+# Calculate the electoral votes for each candidate
+state_predictions$trump_electoral_votes <- ifelse(state_predictions$winner == "Trump", state_predictions$electoral_votes, 0)
+state_predictions$harris_electoral_votes <- ifelse(state_predictions$winner == "Harris", state_predictions$electoral_votes, 0)
+
+# Summarize the total electoral votes for each candidate
+trump_electoral_votes <- sum(state_predictions$trump_electoral_votes)
+harris_electoral_votes <- sum(state_predictions$harris_electoral_votes)
+
+# Create and display the results table
+
+kable(state_predictions[, c("state", "predicted_percent_trump", "electoral_votes", "winner")], 
+      col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"), 
+      digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
+  scroll_box(width = "100%", height = "400px")
+
+print(paste("Trump Electoral Votes:", trump_electoral_votes))
+print(paste("Harris Electoral Votes:", harris_electoral_votes))
+```
+
+## Prediction map
+The following map (Figure 6) displays the predicted outcome for each state in the 2024 U.S.
+Presidential Election, with green representing states where Trump is expected to win and blue for those where Harris is predicted to prevail.
+```{r}
+#| echno: false
+#| label: fig-statemap
+#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
+#| echo: false
+#| warning: false
+#| message: false
+
+# Replace NA values in the 'winner' column with 'Trump'
+#state_predictions$winner[is.na(state_predictions$winner)] <- "Trump"
+
+# "red" for Trump and "blue" for Harris
+state_predictions$winner_color <- ifelse(state_predictions$winner == "Trump", "green", "blue")
+
+# Create a map visualization showing the predicted winner by state
+plot_usmap(data = state_predictions, values = "winner_color", regions = "states") +
+  scale_fill_manual(values = c("green" = "green", "blue" = "blue"), name = "Predicted Winner", labels = c("Harris", "Trump")) +
+  labs(title = "Predicted Winner of the 2024 U.S. Presidential Election by State") +
+  theme(legend.position = "right")
+
+```
+The map illustrates Trump gaining traction across central and southern states, including Texas and Missouri, which have traditionally leaned Republican.
+Meanwhile, Harris holds a solid lead in states along the West Coast and in the Northeast, such as California and New York, regions that have a history of Democratic support.
+
+Several battleground states, including Florida and Ohio, are projected to favor Trump, with a slight advantage that marks a contrast to Harris's stronger leads in places like California.
+The map also shows a number of central states in gray, reflecting either a lack of definitive prediction or insufficient data.
+Overall, the map reveals distinct regional patterns, with Trump expected to perform well in the heartland and Harris finding support along the coasts.
+The outcome may hinge on the final results in the competitive states like Pennsylvania, Arizona, and North Carolina.
 
@@
 
-# Model details {#sec-model-details}
+# Model details 
+```{r}
+# Generate diagnostic plots for model2
+par(mfrow = c(2, 2))
+plot(model2)
+
+# Generate pairwise scatter plots for all predictor variables
+pairs(analysis_data_train[, c("numeric_grade", "duration", "sample_size", "transparency_score")])
+
+```
+```{r}
+
+#  AIC 和 BIC
+AIC_value <- AIC(model2)
+BIC_value <- BIC(model2)
+
+print(paste("AIC: ", AIC_value))
+print(paste("BIC: ", BIC_value))
+
+```
 

### 2024-10-29 scripts/06-model_data.R

@@ -14,7 +14,7 @@ library(rstanarm)
 library(rsample)
 library(dplyr)
 library(car)
-
+library(arrow)
 
 #### Read data ####
 analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")

### 2024-10-29 paper/paper.qmd
update abstract

@@
 date-format: long
-abstract: "In this paper, we built a linear regression model based on \"poll-of-polls\" data to predict the winner of the 2024 U.S.
-By combining data from multiple polls, our model can predict voter preferences more consistently and predict that Donald Trump is likely to win.
-This approach helps reduce the short-term variation present in individual polls and provides a clearer view of long-term electoral trends.
-Our findings contribute to understanding the dynamics of public opinion during election campaigns, which helps the public and political strategists make more informative decisions."
+abstract: "In this paper, we have built a linear model to predict the outcome of the 2024 U.S.
+presidential election, using a \"poll-of-polls\" approach that combines data from many well-known pollsters.
+Our analysis shows that Donald Trump has a probability of winning between 45% and 55%, which depends on how polling data changes from state to state.
+However, Kamala Harris is projected to win key states and receive the majority of electoral votes, with a projected 239 votes to Trump's 98.
+These show the value of aggregate polls in providing reliable predictions of election outcomes."
 format: pdf

### 2024-10-29 paper/paper.qmd
fix git issue and update data and abstract sections

@@
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 library(usmap)
-
+library(patchwork)
 ```
@@
 
-### Percent Support for Donald Trump (pct)
+### Percent Support for Donald Trump
 The primary outcome variable is the percentage (`pct`) of respondents who indicated support for Donald Trump in the 2024 general election.
@@
 ## Predictor variables
-Polling Methodology (methodology)
+
+### Polling Methodology
 The `methodology` variable describes the method each pollster used to collect data.
@@
 
- State (state)
+### State
 The `state` variable identifies whether the poll is state-specific or national.
@@
 
-Polling Score and Transparency (numeric_grade and transparency_score)
+```{r}
+#| label: tbl-state
+#| tbl-cap: "The electoral votes allocated to each U.S. state, listed in two sets for better readability. Each state’s electoral vote count reflects its representation in the Electoral College."
+#| echo: false
+#| warning: false
+
+# Define the number of electoral votes for each state
+electoral_seats <- data.frame(
+  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida",
+            "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", 
+            "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
+            "Missouri", "Montana", "Nebraska", "Nevada", 
+            "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", 
+            "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", 
+            "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", 
+            "District of Columbia"),
+  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
+                      3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
+)
+
+# Split the data into two equal groups (first half and second half)
+half_n <- ceiling(nrow(electoral_seats) / 2)
+states_set1 <- electoral_seats[1:half_n, ]
+states_set2 <- electoral_seats[(half_n + 1):nrow(electoral_seats), ]
+
+# Ensure both sets have the same number of rows by padding the shorter set with NA
+states_set2 <- rbind(states_set2, data.frame(state = "", electoral_votes = ""))
+
+# Combine the two sets into one data frame for side-by-side visualization
+combined_states <- data.frame(
+  state_set1 = states_set1$state,
+  seats_set1 = states_set1$electoral_votes,
+  state_set2 = states_set2$state,
+  seats_set2 = states_set2$electoral_votes
+)
+
+combined_states |>
+  kable(col.names = c("States", "Electoral Votes", "States", "Electoral Votes"))
+```
+
+@tbl-state illustrates the number of electoral votes allocated to each U.S.
+state, based on data from the official government website [@citepollstate].
+This information will be used to map the predicted results for each state later, allowing us to calculate the total number of electoral votes that Donald Trump is projected to receive.
+
+### Polling Score and Transparency
 The `numeric_grade` variable is a rating assigned to each polling organization, indicating the reliability of the poll.
@@
 
- Sample Size (sample_size)
+```{r}
+#| label: fig-poll-score
+#| fig-cap: "Distribution of Polling Scores and Transparency Scores of Polling Organizations in the 2024 U.S. Presidential Election"
+#| echo: false
+#| warning: false
+
+cleaned_data <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))
+
+# Create a bar chart for the distribution of numeric_grade
+p1 <- ggplot(cleaned_data, aes(x = numeric_grade)) +
+  geom_bar(fill = "steelblue", color = "black") +
+  labs(title = "Distribution of Polling Scores",
+       x = "Numeric Grade",
+       y = "Count") +
+  theme_minimal()
+
+# Create a bar chart for the distribution of transparency_score
+p2 <- ggplot(cleaned_data, aes(x = transparency_score)) +
+  geom_bar(fill = "darkorange", color = "black") +
+  labs(title = "Distribution of Transparency Scores",
+       x = "Transparency Score",
+       y = "Count") +
+  theme_minimal()
+
+# Display the two charts side by side using patchwork
+p1 + p2
+
+```
+@fig-poll-score presents two bar charts illustrating the distribution of Polling Scores (Numeric Grades) and Transparency Scores across the polling organizations in the analysis:
+
+- **Polling Scores**: Most organizations have numeric grades between 2.8 and 3.0, indicating that the majority of pollsters are considered highly reliable.
+Very few have grades below 2.7, which would suggest lower reliability.
+
+- **Transparency Scores**: Transparency scores show more variability, with many pollsters achieving scores above 9, reflecting a high level of openness in their methodology.
+Fewer organizations have transparency scores below 6, indicating that while some pollsters are less open, the majority strive for transparency in their practices.
+
+### Sample Size
 The `sample_size` variable represents the total number of respondents surveyed in each poll.
@@
 
- Poll Duration (duration)
+### Poll Duration
 The `duration` variable is a constructed variable that represents how long Donald Trump has been in the 2024 presidential campaign, measured as the number of days from his official campaign announcement on July 15, 2024 until the `end_date` of each poll.
 This variable helps quantify how much time has passed since Trump officially entered the race and allows us to examine how his support has evolved over the course of his campaign.
-
-In summary, the dataset offers a rich variety of variables that capture voter sentiment, pollster reliability, and electoral dynamics.
-By carefully filtering and analyzing this data, we can build a robust model to forecast the outcome of the 2024 US Presidential election.
 

### 2024-10-29 paper/paper.qmd
update introduction

@@
 
-The presidential election has a significant impact on national and global policies, which makes election forecasting a valuable tool for understanding political outcomes.
-However, individual polls often contain biases and short-term fluctuations that can obscure long-term trends.
-To deal with these challenges, we use a ‘poll-of-polls’ approach that combines multiple polls to provide more stable predictions of voter preferences over time.
+The results of presidential elections influence national and international policies and determine governance and economic priorities.
+An accurate election forecast is a valuable tool for political strategists, the media, and the public.
+The 2024 U.S.
+presidential election is expected to be highly competitive, with Donald Trump and Kamala Harris as the leading candidates.
 In this paper, we use national polling data from the period leading up to the 2024 U.S.
-presidential election to generate a logistic model that predicts the winner while capturing changes in public opinion throughout the election period.
+presidential election to generate a linear regression model that predicts the winner while capturing changes in public opinion throughout the election period.
 
-The model estimates the probability of a candidate winning an election based on aggregated polling data.
-Logistic regression is used for binary outcomes such as election results, which allows us to model the likelihood of each candidate winning as new data becomes available.
-By taking into account changes in opinion polls and tracking trends in public opinion over time, this model improves the accuracy of predictions.
+This study estimates the probability of each candidate winning based on aggregate polling data.
+By combining the results, we reduce the bias and short-term volatility of individual polls.
+By using a linear model, we estimate the probability of a Trump victory to be between 45% and 55%, which depends on state-by-state variations.
 
-Our analysis identifies key trends among the major candidates and tracks changes in public sentiment throughout the campaign.
-The results suggest that aggregated polls can reduce some uncertainty by smoothing short-term fluctuations between surveys, but uncertainty cannot be eliminated.
-A sudden change in public opinion can still change the path of an election campaign, which highlights the importance of continuous polling monitoring.
-
-A reliable election forecast can influence public expectations, and campaign strategies, and increase the visibility of reporting on election trends.
-An accurate forecast can also increase voter participation by providing individuals with a clearer perspective of the electoral landscape, and help them participate more effectively in the process of democracy.
-Prediction models like ours not only help with resource allocation for campaigns but also support the wider public by providing them with a clearer understanding of political dynamics.
+Our findings suggest that while Trump has a competitive chance, Harris is projected to win key states and receive a majority of electoral votes.
+Harris will receive 239 electoral votes to Trump's 98 votes.
+This is important because accurate election forecasts help reduce uncertainty, which allows political stakeholders to allocate resources efficiently and gives the public a better understanding of likely outcomes.
+Aggregate polling reduces uncertainty and provides a clearer picture of potential outcomes.
 
@@
 Finally, @sec-discussion provides the results, highlighting key trends and predictions.
-Eventuallt, @sec-discussion concludes with a discussion of the findings, evaluating the reliability of the forecasts and identifying potential limitations of the models.
+Eventually, @sec-discussion concludes with a discussion of the findings, evaluating the reliability of the forecasts and identifying potential limitations of the models.
 

### 2024-10-31 paper/paper.qmd
update prose and reference

@@
 Our modeling approach aims to quantify the relationship between various polling metrics and the percentage support for a candidate.
-For this analysis, we use a linear model (LM) to examine how factors such as poll grade, methodology, poll duration, sample size, transparency score, and state influence support percentages.
+For this analysis, we use a linear model (LM) to examine how factors such as poll score, methodology, poll duration, sample size, transparency score, and state influence support percentages.
 The model is implemented using the lm function, with a Gaussian distribution to capture the variability in support rates.
@@
 In this analysis, we use predictors that reflect both the methodological quality and structural characteristics of each poll.
-Specifically, we include variables such as numeric_grade, which quantifies the poll’s quality, methodology, duration (the length of the election period), sample_size, transparency_score, and state (the regional factor).
-This selection of predictors ensures a comprehensive view of the factors impacting support percentage.
+Specifically, we include variables such as `numeric_grade`, which quantifies the poll’s quality, `methodology`, `duration` (the length of the election period), `sample_size`, `transparency_score`, and `state` (the regional factor).
 
@@
 To prevent overfitting and ensure interpretability, we assume moderate priors, maintaining balanced uncertainty across our predictors.
-This approach enables us to assess the impact of polling characteristics on candidate support while ensuring stability and robustness in our findings.
+This approach enables us to assess the impact of polling characteristics on candidate support while ensuring stability in our findings.
 
 ## Model set-up
-The model now predicts Trump's support percentage using the following predictor variables:
+The model predicts Trump's support percentage using the following predictor variables:
 
-Numeric Grade (numeric_grade): Represents the quality rating of the poll.
+- Poll Score (`numeric_grade`): Represents the quality rating of the poll.
 
-Methodology (methodology): Different methods used to conduct the poll, such as live phone, mixed voting, or online ads.
+- Methodology (`methodology`): Different methods used to conduct the poll, such as live phone, mixed voting, or online ads.
 
-Poll Duration (duration): The the length of the election period was conducted.
+- Poll Duration (`duration`): The the length of the election period was conducted.
 
-Sample Size (sample_size): The number of respondents in the poll.
+- Sample Size (`sample_size`): The number of respondents in the poll.
 
-Transparency Score (transparency_score): A measure of how transparent the polling data and methodology are.
+- Transparency Score (`transparency_score`): A measure of how transparent the polling data and methodology are.
 
-State (state): A categorical variable representing the U.S. state where the poll was conducted.
+- State (`state`): A categorical variable representing the U.S. state where the poll was conducted.
 
@@
     y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
-    \mu_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{methodology}_i \\
-          &\quad + \beta_3 \cdot \text{duration}_i + \beta_4 \cdot \text{sample\_size}_i \\
-          &\quad + \beta_5 \cdot \text{transparency\_score}_i + \beta_6 \cdot \text{state}_i + \epsilon_i \\
+    \mu_i &= \beta_0 + \beta_1 \cdot \text{Poll Score}_i + \beta_2 \cdot \text{Methodology}_i \\
+          &\quad + \beta_3 \cdot \text{Poll Duration}_i + \beta_4 \cdot \text{Sample Size}_i \\
+          &\quad + \beta_5 \cdot \text{Rransparency Score}_i + \beta_6 \cdot \text{State}_i + \epsilon_i \\
     \epsilon_i &\sim \text{Normal}(0, \sigma^2)
@@
 
-The model is executed in R using the \texttt{rstanarm} package.
-Default priors from \texttt{rstanarm} are used, with the priors set to have a mean of zero and a moderate standard deviation to ensure a reasonable level of regularization.
+The model is executed in \texttt{R} [@citeR] using the \texttt{rstanarm} package [@rstanarm].
+Default priors from \texttt{rstanarm} [@rstanarm] are used, with the priors set to have a mean of zero and a moderate standard deviation to ensure a reasonable level of regularization.
 
 ### Model justification
-Existing research and political science theories suggest that factors such as poll quality, sample size, transparency, methodology, poll duration, and the state where the poll takes place can significantly influence Trump's support percentage.
+Existing research and political science theories suggest that factors such as poll quality, sample size, transparency, methodology, poll duration, and the state where the poll takes place can influence Trump's support percentage.
 Higher quality polls and larger sample sizes are believed to yield more reliable estimates, while transparency scores can affect levels of public trust, potentially altering support.
@@
 The model helps us determine the extent to which different aspects of polling influence the level of public support for Trump.
+
+Further justification for using this model comes from its alignment with the central limit theorem, which suggests that with sufficient sample size, the distribution of poll percentages should approximate normality.
+Additionally, the relationships between the predictors (e.g., poll quality, methodology type) and support align well with established theories in political behavior, giving a solid theoretical underpinning to our model.
+The simplicity of a linear regression approach also helps mitigate overfitting, ensuring our results are generalizable to a broader set of polling data.
+
+# Results {#sec-result}
+@sec-result examines the relationship between polling score, methodology, poll duration, transparency score, sample size, and state, with respect to Donald Trump's polling performance in the 2024 U.S.
+Presidential Election.
+Using a dataset that captures polling data across various states and polling organizations, we apply a linear regression model to identify key factors that influence Trump's support.
+Below, we present the results of our model and its implications.
+
+## Model Results and Interpretation
+The linear regression model built by our training dataset, using 384 data points, estimated the factors influencing Trump's support levels.
+As @tbl-summary-model shows, the intercept, estimated at 43.39, represents the level of support when all other predictors are at baseline.
+The model achieved an R-squared value of 0.85, indicating that 85% of the variance in Trump's support percentage can be explained by the predictors included in the model.
+The adjusted R-squared value of 0.82 also shows that the model effectively captures the relationships between variables without overfitting.
+The Root Mean Square Error (RMSE) was 2.03, indicating the average difference between predicted and actual values.
+The relatively low RMSE value suggests that the model provides reasonably accurate predictions.
+
+The results highlight that `numeric_grade` and `sample_size` are particularly important in predicting support levels, with larger and higher-quality polls offering more reliable estimates.
+The transparency score and state-level coefficients further provide understanding into regional differences and the role of trust in polling, helping us better understand the dynamics behind Trump's public support.The coefficients for `numeric_grade` and `sample_size` underline the importance of poll quality and sample size in predicting support levels.
+Larger, higher-quality polls offer more estimates.
+Additionally, transparency and state effects provide insight into regional differences and trust factors affecting polling results, giving a clearer understanding of the dynamics influencing Trump's public support.
+
 ```{r}
 #| label: tbl-summary-model
-#| tbl-cap: Summary of the Linear Regression Model
+#| tbl-cap: "Summary of the Linear Regression Model for Predicting Polling Outcomes"
 #| echo: false
@@
 
-Further justification for using this model comes from its alignment with the central limit theorem, which suggests that with sufficient sample size, the distribution of poll percentages should approximate normality.
-Additionally, the relationships between the predictors (e.g., poll quality, methodology type) and support align well with established theories in political behavior, giving a solid theoretical underpinning to our model.
-The simplicity of a linear regression approach also helps mitigate overfitting, ensuring our results are generalizable to a broader set of polling data.
-The model assumptions, including linearity, independence, and normality of residuals, are adequately satisfied by our dataset, making this approach not only convenient but also statistically robust for our analysis.
-
-# Results {#sec-result}
-## Model Results and Interpretation
-The linear regression model, using 384 data points, estimated the factors influencing Trump's support levels.
-The intercept, estimated at 43.39, represents the level of support when all other predictors are at baseline.The model achieved an R-squared value of 0.85, indicating that 85% of the variance in Trump's support percentage can be explained by the predictors included in the model.
-The adjusted R-squared value of 0.82 also shows that the model effectively captures the relationships between variables without overfitting.The Root Mean Square Error (RMSE) was 2.03, indicating the average difference between predicted and actual values.
-The relatively low RMSE value suggests that the model provides reasonably accurate predictions.The results highlight that numeric_grade and sample_size are particularly important in predicting support levels, with larger and higher-quality polls offering more reliable estimates.
-The transparency score and state-level coefficients further provide insight into regional differences and the role of trust in polling, helping us better understand the dynamics behind Trump's public support.The coefficients for numeric_grade and sample_size underline the importance of poll quality and sample size in predicting support levels.
-Larger, higher-quality polls offer more robust estimates.
-Additionally, transparency and state effects provide insight into regional differences and trust factors affecting polling results, giving a clearer understanding of the dynamics influencing Trump's public support.
-
 ## Predicted Electoral Outcomes
@@
 
-The following table（@predictiontable） presents a summary of the predictions, including Trump’s estimated percentage, the number of electoral votes in each state, and the projected winner.
-For instance:
+@tbl-predictiontable presents a summary of the predictions, including Trump’s estimated percentage, the number of electoral votes in each state, and the projected winner. For instance:
 
- • In Arizona, Trump is expected to receive 48.94% of the vote, resulting in a win for Harris with 11 electoral votes.
- • In Missouri, Trump is projected to receive 51.64%, thereby winning all 10 electoral votes for that state.
- • In Ohio, with an estimated 51.98% of the vote, Trump secures Ohio’s 18 electoral votes.
+- In Arizona, Trump is expected to receive 48.94% of the vote, resulting in a win for Harris with 11 electoral votes.
+- In Missouri, Trump is projected to receive 51.64%, thereby winning all 10 electoral votes for that state.
+- In Ohio, with an estimated 51.98% of the vote, Trump secures Ohio’s 18 electoral votes.
 
@@
 These results hinge on the outcomes in various battleground states, with several being extremely close.
-```{r predictiontable}
-#| echno: false
-#| label: predictiontable
+
+```{r}
+#| label: tbl-predictiontable
 #| tbl-cap: Prediction for Trump and Harris by Electoral College
@@
 ## Prediction map
-The following map (Figure 6) displays the predicted outcome for each state in the 2024 U.S.
+@fig-statemap displays the predicted outcome for each state in the 2024 U.S.
 Presidential Election, with green representing states where Trump is expected to win and blue for those where Harris is predicted to prevail.
 ```{r}
-#| echno: false
 #| label: fig-statemap

### 2024-10-31 paper/paper.qmd
update appendix A

--- 2024-10-29 paper/paper.qmd
@@
 The polling methodology emphasizes live phone interviews and representative sampling and focuses on transparency and statistical accuracy to provide a deep understanding of voter sentiment.
+[@]
 
@@
 The margin of error for likely voters is about ±2.2 percentage points.
+[@]
 
 ## Sample Recruitment
-The sample was conducted by live telephone interviews in both English and Spanish. Over 98% of respondents were contacted by telephone.
+The sample was recruited by telephone.
+Registered voters were selected from the voter files held by L2 and contacted via their listed telephone numbers including landlines and mobile phone numbers.
+More than 260,000 calls were made to more than 80,000 voters, with over 98% of respondents using mobile phones.
+Interviews were conducted by live telephone interviews in both English and Spanish.\ [@]
 
@@
 ## Non-response Handling
-Non-response was a key problem for Siena/NYT.
-The poll used weighted adjustments for demographic characteristics such as age, race, gender, education, and different political parties to address non-response bias.
-The weighting adjustment was used to ensure that the sample closely matches the larger population and compensates for differences in response rates across demographic groups.
-However, non-response can still present residual bias even with weighting, especially when certain demographic groups have been less likely to respond to survey calls.
+
+**Weighting adjustment:** The Times weighted the sample using the survey software package in R and adjusted for unequal probability of selection in each stratum.
+The sample was also split by political party and weighted according to parameters of registered voter characteristics from the voter file.
+This weighting step ensures that respondents from underrepresented demographic groups such as those without a college degree are given more weight so that the results reflect the voting population overall.\
+
+**Non-Response Model:** To adjust for non-response bias, the L2 voter file was stratified by ‘state precinct,’ ‘political party,’ ‘race,’ ‘gender,’ ‘marital status,’ and ‘voting history.’ The average expected response rate is based on a single-place non-response rate model from previous Siena/NYT surveys, which can be adjusted appropriately to account for different response rates in different groups.\
+
+**Multiple calls and language adaptation:** Interviewers made more than 260,000 calls to more than 80,000 voters, resulting in a sample of 2,516 respondents.
+Interviewers conducted the interviews in English and Spanish, and bilingual interviewers adapted the language of the interviews to respondent preferences, which helped to increase the participation of Spanish-speaking respondents.
+Re-contacts by interviewers reduced the non-response rate.
 

### 2024-10-31 scripts/00-simulate_data.R
update scripts' preamble

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset of 2024 US election, to explore 
+  #what plausible values might appear in the dataset.
+# Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
+# Date: 30 October 2024
+# Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Workspace setup ####

### 2024-10-31 scripts/01-test_simulated_data.R

@@ -1,14 +1,14 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated 2024 US  
+  #election dataset.
+# Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
+# Date: 30 October 2024
+# Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
   # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Workspace setup ####

### 2024-10-31 scripts/02-download_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from FiveThirtyEight
+# Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
+# Date: 30 October 2024
+# Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
+# Any other information needed? None
 
 
 #### Workspace setup ####

### 2024-10-31 scripts/03-clean_data.R

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw election data
+# Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
+# Date: 30 October 2024
+# Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
+# Any other information needed? None
+
 
 #### Workspace setup ####
 library(arrow)

### 2024-10-31 scripts/04-test_analysis_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests structure of the analysis data 
+# Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
+# Date: 30 October 2024
+# Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
+# Any other information needed? None
 
 
 #### Workspace setup ####

### 2024-10-31 scripts/05-exploratory_data_analysis.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models US presidential election polls by using GLM 
+# Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
+# Date: 30 October 2024
+# Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
+# Any other information needed? None
 
 
 #### Workspace setup ####

### 2024-10-31 scripts/06-model_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models US presidential election polls by using LM, and compare two regression models
+# Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
+# Date: 30 October 2024
+# Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
+# Any other information needed? None
 
 
 #### Workspace setup ####

### 2024-10-31 scripts/07-install_packages.R

@@ -1,11 +1,12 @@
 #### Preamble ####
 # Purpose: Install necessary packages
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
-# Date: 26 September 2024
-# Contact: leoy.liu@mail.utoronto.ca
+# Date: 30 October 2024
+# Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: None
 # Any other information needed? None
+
 
 
 #### Install packages ####

### 2024-10-31 paper/paper.qmd
update paper content, and check appendix format

@@
 presidential election, using a \"poll-of-polls\" approach that combines data from many well-known pollsters.
-Our analysis shows that Donald Trump has a probability of winning between 45% and 55%, which depends on how polling data changes from state to state.
-However, Kamala Harris is projected to win key states and receive the majority of electoral votes, with a projected 239 votes to Trump's 98.
+Our analysis shows that Donald Trump has a probability of winning in range 45% to 55% in each state, which depends on how polling data changes from state to state.
+However, Kamala Harris is projected to win key states and receive the majority of electoral votes, with a projected 239 votes to Trump's 98, based on testing dataset, we only have those state in the dataset.
 These show the value of aggregate polls in providing reliable predictions of election outcomes."
@@
 Eventually, @sec-discussion concludes with a discussion of the findings, evaluating the reliability of the forecasts and identifying potential limitations of the models.
+
+## Estimand
+Todo:
 
@@
                       3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3))
+
 # Convert methodology column to character type for recoding
@@
 analysis_data_test$predicted_percent_trump <- predict(model2, newdata = analysis_data_test)
-analysis_data_test$predicted_percent_trump
 total_trump <- aggregate(predicted_percent_trump ~ state, data = analysis_data_test, FUN = mean)
@@
 # Create and display the results table
-
 kable(state_predictions[, c("state", "predicted_percent_trump", "electoral_votes", "winner")], 
@@
   scroll_box(width = "100%", height = "400px")
-
-print(paste("Trump Electoral Votes:", trump_electoral_votes))
-print(paste("Harris Electoral Votes:", harris_electoral_votes))
 ```
@@
 #| label: fig-statemap
-#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
+#| fig-cap: Predicted Winner of 2024 US Presidential Election by State
 #| echo: false
@@
 #| message: false
-
-# Replace NA values in the 'winner' column with 'Trump'
-#state_predictions$winner[is.na(state_predictions$winner)] <- "Trump"
 
@@
 The outcome may hinge on the final results in the competitive states like Pennsylvania, Arizona, and North Carolina.
-
-Our results are summarized in @tbl-modelresults.
 
@@
 # Pollster Methodology Overview and Evaluation
+
 ## Overview of Siena/NYT
@@
 ## Target Population, Frame, and Sample
-* Target Population: Registered voters or likely voters in the United States, especially voters in major battleground states during an election in 2024.\
-* Sample Frame: U.S. registered voters based on a national voter file maintained by L2, with a cell phone number that matches the voter file.\
+* Target Population: Registered voters or likely voters in the United States, especially voters in major battleground states during an election in 2024.
+* Sample Frame: U.S. registered voters based on a national voter file maintained by L2, with a cell phone number that matches the voter file.
 * Sample Size: Sample sizes vary across different polls.
@@
 More than 260,000 calls were made to more than 80,000 voters, with over 98% of respondents using mobile phones.
-Interviews were conducted by live telephone interviews in both English and Spanish.\ [@]
+Interviews were conducted by live telephone interviews in both English and Spanish.
+[@]
 
@@
 This improves accuracy but adds cost and complexity.
-It also makes it challenging to reach certain populations such as young voters.\
+It also makes it challenging to reach certain populations such as young voters.
 
-**Advantages of stratified sampling:**\
+**Advantages of stratified sampling:**
 
-* Generates a representative sample that captures the diverse opinions of different voter populations.\
-* Helps to ensure that under-represented groups are given appropriate weighting, and reduces potential bias.\
-* Provides a more accurate reflection of the wider population by stratifying on key characteristics.\
+* Generates a representative sample that captures the diverse opinions of different voter populations.
+* Helps to ensure that under-represented groups are given appropriate weighting, and reduces potential bias.
+* Provides a more accurate reflection of the wider population by stratifying on key characteristics.
 
-**Disadvantages of stratified sampling:**\
+**Disadvantages of stratified sampling:**
 
-* Increased cost and time to complete polls, especially for live telephone interviews.\
-* There are challenges in reaching specific demographic groups, such as younger voters who may be less likely to participate in the poll.\
+* Increased cost and time to complete polls, especially for live telephone interviews.
+* There are challenges in reaching specific demographic groups, such as younger voters who may be less likely to participate in the poll.
 * Reliance on weighting adjustments to correct for response discrepancies, which does not fully eliminate residual bias.
@@
 The sample was also split by political party and weighted according to parameters of registered voter characteristics from the voter file.
-This weighting step ensures that respondents from underrepresented demographic groups such as those without a college degree are given more weight so that the results reflect the voting population overall.\
+This weighting step ensures that respondents from underrepresented demographic groups such as those without a college degree are given more weight so that the results reflect the voting population overall.
 
-**Non-Response Model:** To adjust for non-response bias, the L2 voter file was stratified by ‘state precinct,’ ‘political party,’ ‘race,’ ‘gender,’ ‘marital status,’ and ‘voting history.’ The average expected response rate is based on a single-place non-response rate model from previous Siena/NYT surveys, which can be adjusted appropriately to account for different response rates in different groups.\
+**Non-Response Model:** To adjust for non-response bias, the L2 voter file was stratified by 'state precinct', 'political party', 'race', 'gender', 'marital status', and 'voting history'.
+The average expected response rate is based on a single-place non-response rate model from previous Siena/NYT surveys, which can be adjusted appropriately to account for different response rates in different groups.
 
@@
 ## Questionnaire Evaluation
-**Strengths:**\
 
-* Minimize bias through the use of straightforward and non-leading questions.\
-* Transparency was maintained by publishing the questions verbatim to allow for public scrutiny.\
-* Bilingual interviewers ensured that respondents could participate in their preferred language (English or Spanish), which increased the participation of Spanish-speaking voters and improved the quality of respondents' answers.\
+**Strengths:**
 
-**Weaknesses:**\
+* Minimize bias through the use of straightforward and non-leading questions.
+* Transparency was maintained by publishing the questions verbatim to allow for public scrutiny.
+* Bilingual interviewers ensured that respondents could participate in their preferred language (English or Spanish), which increased the participation of Spanish-speaking voters and improved the quality of respondents' answers.
 
-* The length of the poll can lead to respondent fatigue, which affects the quality of the data and increases dropout rates.\
-* It can be challenging to limit calls to less than 15 minutes, which can lead to incomplete or rushed responses, thus affecting the overall reliability of the data.\
+**Weaknesses:**
+
+* The length of the poll can lead to respondent fatigue, which affects the quality of the data and increases dropout rates.
+* It can be challenging to limit calls to less than 15 minutes, which can lead to incomplete or rushed responses, thus affecting the overall reliability of the data.
 
@@
 While the use of composite weighting and bilingual interviews provides advantages such as transparency and reduced bias, challenges remain including high costs and the potential for bias due to non-response.
-Despite these drawbacks, Siena/NYT's commitment to transparency and rigorous methodology makes it a reliable source for understanding voter sentiment and opinion.\
+Despite these drawbacks, Siena/NYT's commitment to transparency and rigorous methodology makes it a reliable source for understanding voter sentiment and opinion.
 
 # Idealized Methodology and Survey
+
 ## Overview
@@
 ### Stratification Variables 
-* Age: 18-29, 30-44, 45-64, 65+\
-* Gender: Male and Female\
-* Race: White, Black /African American, Hispanic/Latino, Asian, Native and Other\
-* Education level: High School, Some College, Bachelor's Degree, Graduate Degree, Other\
-* Geographic region: Northeast, Midwest, South, West\
-* Political Party: Democratic, Republican, Independent, Other\
+* Age: 18-29, 30-44, 45-64, 65+
+* Gender: Male, Female, Non-binary
+* Race: White, Black /African American, Hispanic/Latino, Asian, Native, Other
+* Education level: High School, Some College, Bachelor's Degree, Graduate Degree, Other
+* Geographic region: Northeast, Midwest, South, West
+* Political Party: Democratic, Republican, Independent, Other
 
@@
 
-**Online Survey panels:**\
+**Online Survey panels:**
 
-* Work with established survey panels such as Lucid or YouGov.\
-* These panels have access to large representative databases of voters.\
-* Recruiting through panels ensures quality and reliability, as they have built-in validation and quality control processes.\
+* Work with established survey panels such as Lucid or YouGov.
+* These panels have access to large representative databases of voters.
+* Recruiting through panels ensures quality and reliability, as they have built-in validation and quality control processes.
 
-**Social Media Advertising:**\
+**Social Media Advertising:**
 
-* Use social media platforms such as Facebook, Instagram and LinkedIn to reach potential respondents.\
-* Target groups that are underrepresented in traditional panels, including young voters and minority groups.\
-* Social media ads will be customized with demographic information to increase reach and participation.\
+* Use social media platforms such as Facebook, Instagram and LinkedIn to reach potential respondents.
+* Target groups that are underrepresented in traditional panels, including young voters and minority groups.
+* Social media ads will be customized with demographic information to increase reach and participation.
 
@@
 ## Data validation and quality control
-To maintain the integrity of the data, we will take the following measures:\
+To maintain the integrity of the data, we will take the following measures:
 
-* **Attention Checks:** At least two ‘attention check’ questions will be included in the survey to identify inattention or robots.\
-* **Duplicate Detection:** Use email or IP-based verification to prevent duplicate responses. Ensure that each respondent provides only one response set to keep the dataset unique.\
-* **Response Time Monitoring:** Track the time it takes respondents to complete surveys. Responses with apparently faster-than-average completion times are labelled as potentially low-quality.\
-* **Data Consistency Check:** Analyses the consistency of responses, especially between related questions. Inconsistent answers will be labelled for review.\
+* **Attention Checks:** At least two 'attention check' questions will be included in the survey to identify inattention or robots.
+* **Duplicate Detection:** Use email or IP-based verification to prevent duplicate responses. Ensure that each respondent provides only one response set to keep the dataset unique.
+* **Response Time Monitoring:** Track the time it takes respondents to complete surveys. Responses with apparently faster-than-average completion times are labelled as potentially low-quality.
+* **Data Consistency Check:** Analyses the consistency of responses, especially between related questions. Inconsistent answers will be labelled for review.
 * **Panel partner validation:** For respondents recruited through an online survey panel, rely on the panel provider's in-built validation systems.
@@
 ### Poll aggregation
-* ‘Poll of polls’ approach: Survey data will be combined with data from some reliable polling sources such as Lucid, YouGov and others.
-This approach aggregates the results of multiple reputable polls to improve the forecast reliability by reducing bias and individual polling errors.\
+* 'Poll of polls' approach: Survey data will be combined with data from some reliable polling sources such as Lucid, YouGov and others.
+This approach aggregates the results of multiple reputable polls to improve the forecast reliability by reducing bias and individual polling errors.
 * Weighting adjustments: Polls are weighted according to sample quality, size, repeatability, and demographic match.
@@
 This approach allows for dynamic updating as new data becomes available, which improves accuracy.
-\
 * Uncertainty Quantification: Includes confidence intervals to express uncertainty in forecasts for a more detailed interpretation.
@@
 ## Budget Allocation
-* Survey Panel Recruitment: $50,000\
-* Social Media Advertising: $50,000\
-* Incentives(lottery prizes): $15,000\ 
-* Data Cleaning and Validation: $5,000\
+* Survey Panel Recruitment: $50,000
+* Social Media Advertising: $50,000
+* Incentives(lottery prizes): $15,000 
+* Data Cleaning and Validation: $5,000
 * Poll Aggregation and Modeling: $10,000
@@
 To ensure maximum reach and diversity, multiple channels will be used, including Facebook, Instagram, and other social media platforms.
-The link to the survey is [here](https://forms.gle/y4Xh2oQ544DYcCXWA).\
+The link to the survey is [here](https://forms.gle/y4Xh2oQ544DYcCXWA).
 
-**Distribution Plan:**\
+**Distribution Plan:**
 
-* **Panel invitations:** Members of established survey panels (e.g. Lucid, YouGov) will receive email invitations to participate in the survey.\
-* **Social media activities:** Targeted adverts will be placed on social media platforms to reach under-represented groups, especially young voters and national minority groups.\
-* **Follow-up reminders:** An automated reminder email will be sent to participants who have not completed the survey to maximize response rates.\
-* **Survey Monitoring:** Response rates will be closely monitored throughout the data collection period and sampling methods will be adjusted if certain population quotas are not reached.\
+* **Panel invitations:** Members of established survey panels (e.g. Lucid, YouGov) will receive email invitations to participate in the survey.
+* **Social media activities:** Targeted adverts will be placed on social media platforms to reach under-represented groups, especially young voters and national minority groups.
+* **Follow-up reminders:** An automated reminder email will be sent to participants who have not completed the survey to maximize response rates.
+* **Survey Monitoring:** Response rates will be closely monitored throughout the data collection period and sampling methods will be adjusted if certain population quotas are not reached.
 * **Accessibility:** The survey will be mobile-friendly, which will allow respondents to complete the survey on any device.
@@
 ## Survey Structure
-**Survey Introduction:**\
+
+**Survey Introduction:**
 Welcome!
@@
 It will take approximately 10 minutes to complete the survey.
-All responses are confidential and will be used for research purposes only.\
-If you have any questions or concerns, please feel free to contact our research team at [winniekeai23@gmail.com](mailto:winniekeai23@gmail.com) (Ziyuan Shen, Leo Liu, Dezhen Chen).\
+All responses are confidential and will be used for research purposes only.
+
+If you have any questions or concerns, please feel free to contact our research team at [winniekeai23@gmail.com](mailto:winniekeai23@gmail.com) (Ziyuan Shen, Yuanyi (Leo) Liu, Dezhen Chen).
+
 As a thank you for your participation, you will be entered into a raffle to win a grand prize of a gift card.
-We are deeply grateful for your participation and appreciate the time and effort that you put in.\
+We are deeply grateful for your participation and appreciate the time and effort that you put in.
 
-**Survey Question:**\
+**Survey Question:**
 
-**Part 1: Screening for eligibility**\
+**Part 1: Screening for eligibility**
+
 1.Are you an eligible U.S. citizen?\
@@
 2.Are you currently 18 years of age or older?\
-* Yes / No
+* Yes / No\
 3.Have you completed your registration to become a voter?\
-* Yes / No / Plan to register\
+* Yes / No / Plan to register
 
-**Part 2: Demographics**\
+**Part 2: Demographics**
 
@@
 8.Do you generally identify with a political party?\
-* Democratic / Republican / Independent / None\
+* Democratic / Republican / Independent / None
 
-**Part 3: Voting Intentions**\
+**Part 3: Voting Intentions**
 
@@
 11.What are the top three issues that will influence your vote?\
-* Economy / Healthcare / Education / Gun Policy / Taxes / Foreign Policy / Social Security / Civil Rights / Technology / Privacy / Other[text]\
+* Economy / Healthcare / Education / Gun Policy / Taxes / Foreign Policy / Social Security / Civil Rights / Technology / Privacy / Other[text]
 
-**Part 4: Information Sources and Engagement**\
+**Part 4: Information Sources and Engagement**
 
@@
 13.How often do you engage in discussions about political topics with friends or family?\
-* Daily / Weekly / Monthly / Rarely / Never\
+* Daily / Weekly / Monthly / Rarely / Never
 
-**Part 5: Verify**\
+**Part 5: Verify**
 
@@
 15.Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.\
-* Yes / No\
+* Yes / No
 
-**End Part:**\
-Thank you for your participation!\
+**End Part:**
+
+Thank you for your participation!
+
 Your responses are valuable to us in anticipating the upcoming election and understanding voters' priorities.
-If you have any questions or would like more information about our research, please feel free to contact us at [winniekeai23@gmail.com](mailto:winniekeai23@gmail.com)(Ziyuan Shen, Leo Liu, Dezhen Chen).
-
-# Additional data details
+If you have any questions or would like more information about our research, please feel free to contact us at [winniekeai23@gmail.com](mailto:winniekeai23@gmail.com)(Ziyuan Shen, Yuanyi (Leo) Liu, Dezhen Chen).
 
@@
 ```{r}
+#| label: fig-qq-check
+#| fig-cap: Model Diagnosis
+#| echo: false
+#| warning: false
+#| message: false
+
 # Generate diagnostic plots for model2
@@
 pairs(analysis_data_train[, c("numeric_grade", "duration", "sample_size", "transparency_score")])
-
-```
-```{r}
-
-#  AIC 和 BIC
-AIC_value <- AIC(model2)
-BIC_value <- BIC(model2)
-
-print(paste("AIC: ", AIC_value))
-print(paste("BIC: ", BIC_value))
-
-```
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
 ```

### 2024-10-31 paper/paper.qmd
update scripts, correct intro and abstract, update reference

@@
 date-format: long
-abstract: "In this paper, we have built a linear model to predict the outcome of the 2024 U.S.
-presidential election, using a \"poll-of-polls\" approach that combines data from many well-known pollsters.
-Our analysis shows that Donald Trump has a probability of winning in range 45% to 55% in each state, which depends on how polling data changes from state to state.
-However, Kamala Harris is projected to win key states and receive the majority of electoral votes, with a projected 239 votes to Trump's 98, based on testing dataset, we only have those state in the dataset.
-These show the value of aggregate polls in providing reliable predictions of election outcomes."
+abstract: "In this paper, we develop a linear model to predict the outcome of the 2024 U.S.
+presidential election using a \"poll-of-polls\" approach that combines data from various prominent pollsters.
+Our analysis indicates that Donald Trump’s probability of winning varies between 45% and 55% across states, depending on regional polling trends.
+However, Kamala Harris is projected to secure key states and achieve a majority of electoral votes, with a projected count of 239 to Trump’s 98 based on the testing dataset.
+These predictions are based on the testing dataset, which lacks data for some states, limiting our ability to produce results for all states.
+This paper underscore the effectiveness of aggregated polls in producing reliable election forecasts."
 format: pdf
@@
 presidential election is expected to be highly competitive, with Donald Trump and Kamala Harris as the leading candidates.
-In this paper, we use national polling data from the period leading up to the 2024 U.S.
-presidential election to generate a linear regression model that predicts the winner while capturing changes in public opinion throughout the election period.
-
-This study estimates the probability of each candidate winning based on aggregate polling data.
-By combining the results, we reduce the bias and short-term volatility of individual polls.
-By using a linear model, we estimate the probability of a Trump victory to be between 45% and 55%, which depends on state-by-state variations.
+Despite the abundance of polling data, individual polls are often subject to bias and short-term fluctuations, making it difficult to predict election outcomes with confidence.
+This paper addresses this issue by using aggregate polling data to provide more reliable predictions of election outcomes.
 
@@
 ## Estimand
-Todo:
+
+In this study, our estimand is Donald Trump's percentage of polling in each state ahead of the 2024 U.S.
+presidential election.
+The object of the estimation is Trump's percentage of polling data in each state based on aggregated information from various sources By using a linear regression model, we aim to capture changes in public opinion over time and provide a clearer understanding of voter preferences and the likely election outcome.
 
@@
 # Results {#sec-result}
+
 @sec-result examines the relationship between polling score, methodology, poll duration, transparency score, sample size, and state, with respect to Donald Trump's polling performance in the 2024 U.S.
@@
 Below, we present the results of our model and its implications.
+
+We predicted the outcome based on our test dataset.
+However, due to missing data for certain states in our original dataset, we were unable to make predictions for all states.
+This limitation arises because the states with NA values in the dataset are not represented in the model, preventing accurate forecasts for those regions.
 
@@
 ## Prediction map
-@fig-statemap displays the predicted outcome for each state in the 2024 U.S.
-Presidential Election, with green representing states where Trump is expected to win and blue for those where Harris is predicted to prevail.
+
 ```{r}
@@
 # "red" for Trump and "blue" for Harris
-state_predictions$winner_color <- ifelse(state_predictions$winner == "Trump", "green", "blue")
+state_predictions$winner_color <- ifelse(state_predictions$winner == "Trump", "red", "blue")
 
@@
 plot_usmap(data = state_predictions, values = "winner_color", regions = "states") +
-  scale_fill_manual(values = c("green" = "green", "blue" = "blue"), name = "Predicted Winner", labels = c("Harris", "Trump")) +
+  scale_fill_manual(values = c("red" = "red", "blue" = "blue"), name = "Predicted Winner", labels = c("Harris", "Trump")) +
   labs(title = "Predicted Winner of the 2024 U.S. Presidential Election by State") +
@@
 ```
+@fig-statemap displays the predicted outcome for each state in the 2024 U.S.
+Presidential Election, with green representing states where Trump is expected to win and blue for those where Harris is predicted to prevail.
+
 The map illustrates Trump gaining traction across central and southern states, including Texas and Missouri, which have traditionally leaned Republican.
@@
 
-## First discussion point {#sec-first-point}
+## Interpretation of Polling Data and Electoral Implications
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+This paper examines the factors affecting Donald Trump’s polling performance in the 2024 U.S.
+Presidential Election.
+Our linear regression model shows that poll duration and state-specific factors are the strongest predictors of Trump’s support.
+Longer poll durations tend to produce more stable data by capturing changes in public sentiment over time rather than short-term reactions.
+The state variable underscores the importance of local dynamics, as individual states bring unique policy priorities and demographic trends to their voter bases.
+These regional distinctions are essential in the Electoral College system, where state-level support directly impacts the final electoral count.
 
-## Second discussion point
+Transparency and sample size play secondary roles in data reliability.
+Polls with high transparency scores provide clear information about methodology, making them more reliable for analysis.
+Larger sample sizes reduce margins of error, adding stability to projections, especially in closely contested states.
+While both transparency and sample size support reliable predictions, they have less influence on voter preferences than duration and state-specific factors.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+In comparison, polling methodology (e.g., live phone, online) and numeric grade (a general reliability rating) have minimal impact on Trump’s support in our model.
+Although these factors contribute to overall data quality, they do not significantly shape voter sentiment.
+This finding suggests that regional context and polling consistency over time are more important in understanding Trump’s polling performance in this election than the specific techniques or reputations of polling organizations.
 
-## Third discussion point
+## Influence of State Policies on Voter Preferences
 
-## Weaknesses and next steps
+Beyond the mechanics of polling, our analysis suggests that state-specific policies and regional cultural factors could influence voter preferences and ultimately shape electoral outcomes.
+For instance, certain policies, such as the legalization of recreational marijuana, reflect broader ideological values that may correlate with support for particular candidates.
+Although our model does not directly analyze the impact of marijuana policies, including these cultural aspects could offer a more comprehensive view of voter alignment.
 
-Weaknesses and next steps should also be included.
+States with legal recreational marijuana, for example, might lean more progressive or libertarian, potentially aligning with candidates like Harris who advocate for policies seen as liberal or socially progressive.
+This policy environment might signal broader state values that align with a particular party's stance, beyond just the specific candidate.
+Conversely, states that prohibit recreational marijuana use may lean more conservative, suggesting they may have stronger support for Trump.
+Although this relationship is not absolute, understanding such cultural factors helps contextualize the state-level support each candidate may receive and could be valuable in identifying battleground states.
+Additionally, factors like local economic policies, educational investment, or healthcare reform could influence voter preferences, making these areas ripe for future analysis.
+
+## Limitations of the Data and Model
+
+One limitation of this study is the incomplete dataset, with some states missing from the polling data.
+This limits our ability to produce a fully accurate prediction, as certain areas are excluded from the model.
+Additionally, the focus on state-level data may overlook finer voting patterns within states, particularly in districts with unique political identities.
+
+## Future Research Directions
+
+Future studies could improve by incorporating demographic variables such as age, income, and party affiliation, which might offer a clearer understanding of voter preferences.
+Examining additional state-level policies, like healthcare or education, may also provide insights into factors shaping voter choices.
+
+Another possible enhancement involves increasing the geographic specificity of the model to include congressional districts or smaller regions, which may lead to more precise forecasts, especially in competitive states.
+As polling data collection methods evolve, combining traditional regression with machine learning techniques could allow for models that adapt to ongoing changes in public opinion, resulting in more timely and adaptable forecasts.
 
@@
 Siena College Research Institute (SCRI) and The New York Times launched a collaborative political poll in July 2013.
-Siena/NYT  was known for its rigorous methodology and accuracy, which provided its first real-time midterm election poll in 2018.In 2024, FiveThirtyEight named it the most accurate pollster in the United States.
+Siena/NYT  was known for its rigorous methodology and accuracy, which provided its first real-time midterm election poll in 2018 [@citeNYT].
+In 2024, FiveThirtyEight named it the most accurate pollster in the United States.
 The polling methodology emphasizes live phone interviews and representative sampling and focuses on transparency and statistical accuracy to provide a deep understanding of voter sentiment.
-[@]
 
@@
 The margin of error for likely voters is about ±2.2 percentage points.
-[@]
 
@@
 Interviews were conducted by live telephone interviews in both English and Spanish.
-[@]
 
 ## Sampling Approach and Trade-offs
-Siena/NYT used a stratified sampling method.
+Siena/NYT used a stratified sampling method [@citeNYT].
 Polls were stratified by demographic characteristics such as political party, race and region.
@@
 ### Sample Size
-The target sample size was 10,000 respondents, which are stratified by the Stratification Variables described above.
+The target sample size was 5,000 respondents, which are stratified by the Stratification Variables described above.
 This stratification ensures that all major voter groups are proportionately represented.
-10,000 samples have a margin of error of about ±1% and a confidence level of 95%, which is appropriate for predicting elections.
+5,000 samples have a margin of error of about ±1% and a confidence level of 95%, which is appropriate for predicting elections.
 

### 2024-10-31 scripts/00-simulate_data.R

@@ -1,6 +1,5 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of 2024 US election, to explore 
-  #what plausible values might appear in the dataset.
+# Purpose: Simulates a dataset of 2024 US election, to explore what plausible values might appear in the dataset.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca

### 2024-10-31 scripts/01-test_simulated_data.R

@@ -1,6 +1,5 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated 2024 US  
-  #election dataset.
+# Purpose: Tests the structure and validity of the simulated 2024 US election dataset.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca

### 2024-10-31 scripts/05-exploratory_data_analysis.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Models US presidential election polls by using GLM 
+# Purpose: Models US presidential election polls by using LM 
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
@@ -13,25 +13,35 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
-
-
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
+numeric_vars_analysis <- c('numeric_grade', 'transparency_score', 'sample_size', 'pct')
+for (var in numeric_vars_analysis) {
+  p1 <- ggplot(analysis_data, aes(x = !!sym(var))) +
+    geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) +
+    ggtitle(paste("Histogram of", var)) +
+    theme_minimal() +
+    xlab(var) +
+    ylab("Frequency")
+  print(p1) 
+}
 
 
+numeric_vars_electoral <- c('duration', 'num_trump')
+for (var in numeric_vars_electoral) {
+  p <- ggplot(electoral_votes, aes(x = !!sym(var))) +
+    geom_histogram(binwidth = 5, fill = "lightgreen", color = "black", alpha = 0.7) +
+    ggtitle(paste("Histogram of", var)) +
+    theme_minimal() +
+    xlab(var) +
+    ylab("Frequency")
+  print(p)  
+}
+
+p_numeric_grade <- ggplot(analysis_data, aes(x = numeric_grade)) +
[…]

### 2024-10-31 paper/paper.qmd
update scripts and appendix

@@
 library(ggplot2)
-library(kableExtra)
 library(modelsummary)
 library(rstanarm)
-library(modelsummary)
 library(arrow)
@@
 Following methodologies discussed by "Telling Stories with Data" [@tellingstories], we forecast election outcomes using the "poll of polls" method, which aggregates results from multiple polls to reduce bias and provide a more accurate representation of voter sentiment.
+For key operations, please refer to [Appendix -@sec-data-cleaning].
 
@@
 
+# Data Manipulation and Cleaning {#sec-data-cleaning}
+
+In the data cleaning process, we prepared the raw election data for analysis by applying transformations, filtering, and restructuring using several R packages, including `dplyr` [@citedplyr], `janitor` [@citejanitor], `tidyverse` [@citetidyverse], `arrow` [@citearrow], and `rsample` [@citersample].
+
+1. **Standardizing Column Names**: Using the `clean_names()` function, we converted column names to a consistent lowercase format, making them easier to reference and manipulate.
+
+2.
+**Filtering Polls by Quality and Candidate**: With the `dplyr` package from `tidyverse`, we filtered the dataset to include only higher-quality polls with a `numeric_grade` of 2.5 or above, ensuring that only credible polls were considered.
+We further filtered to focus on polls related specifically to Donald Trump (`candidate_name == "Donald Trump"`), aligning the dataset with our analysis objective.
+
+3.
+**Date Conversion and Filtering**: We converted the `end_date` column to a Date format using `mdy()` from `lubridate` (part of `tidyverse`), ensuring date consistency.
+We then filtered the data to include only polls conducted after July 15, 2024—the date of Trump’s campaign announcement—allowing us to focus on his active campaign period.
+
+4. **Creating Duration and Support Columns**:
+   - **Duration**: We created a `duration` variable using the `difftime()` function from base `R`, which calculates the number of days between each poll’s end date and Trump’s campaign start date.
+This allows us to observe how polling data shifts over time.
+   - **Number of Trump Supporters**: We calculated `num_trump`, the estimated number of respondents supporting Trump in each poll, by applying the support percentage (`pct`) to the sample size and rounding the result with `dplyr` functions.
+
+5.
+**Methodology Update**: We used `str_detect()` from `stringr` (in `tidyverse`) to identify polls that listed multiple polling methods (e.g., those containing “/”) and standardized them to "Mixed Voting" to clarify the `methodology` column.
+
+6.
+**Selecting and Renaming Columns**: We used `dplyr` functions to select the relevant columns (`poll_id`, `numeric_grade`, `methodology`, `transparency_score`, `end_date`, `sample_size`, `pollster_name` (renamed from `display_name`), `state`, `pct`, `duration`, and `num_trump`), streamlining the dataset for analysis.
+
+7.
+**Removing Duplicates and Missing Values**: With `dplyr`, we removed duplicate rows using `distinct()` and dropped rows with missing values using `drop_na()`, ensuring that only complete and unique data entries were retained.
+
+8.
+**Splitting the Data**: We utilized `rsample` to perform a stratified split on the cleaned dataset, using the `state` variable to ensure balanced representation across states.
+The data was divided into training (70%) and testing (30%) sets, preparing it for modeling.
+
+Finally, we saved the cleaned dataset and the training/testing splits in CSV and Parquet formats using `arrow`, facilitating efficient storage and future accessibility.
+
 # Model details 

### 2024-10-31 scripts/00-simulate_data.R

@@ -14,38 +14,154 @@ set.seed(853)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
+#determine the number of observations
+num_obs <- 1000
+
+#pollster names
+pollster <- c(
+  "The New York Times/Siena College", 
+  "ABC News/The Washington Post", 
+  "Marquette University Law School", "YouGov",
+  "Monmouth University Polling Institute", 
+  "Marist College", "Suffolk University","Data Orbital", 
+  "University of Massachusetts Lowell Center for Public Opinion", 
+  "Emerson College", 
+  "Muhlenberg College Institute of Public Opinion", 
+  "Selzer & Co.", 
+  "University of North Florida Public Opinion Research Lab", 
+  "CNN","SurveyUSA", "Beacon Research/Shaw & Co. Research", 
+  "Quinnipiac University", "MassINC Polling Group", "Ipsos", 
+  "Christopher Newport University Wason Center for Civic Leadership", 
+  "Siena College","AtlasIntel", "Echelon Insights", 
+  "The Washington Post/George Mason University Schar School of Policy and Government", 
+  "East Carolina University Center for Survey Research", 
+  "Data for Progress", 
+  "Hart Research Associates/Public Opinion Strategies",
+  "University of New Hampshire Survey Center", 
+  "Stockton University William J. Hughes Center for Public Policy", 
+  "Remington Research Group", 
+  "Mason-Dixon Polling & Strategy",
+  "Roanoke College Institute for Policy and Opinion Research", 
+  "Fairleigh Dickinson University", 
+  "University of Arkansas Department of Political Science", 
+  "Lake Research Partners/The Tarrance Group",
+  "Public Policy Institute of California", 
+  "Michigan State University Institute for Public Policy and Social Research",
+  "Elon University", 
+  "Southern Illinois University Paul Simon Public Policy Institute", 
+  "Pew Research Center",
+  "University of Illinois Springfield Survey Research Office", 
+  "Western New England University Polling Institute", 
[…]

### 2024-10-31 scripts/01-test_simulated_data.R

@@ -13,10 +13,10 @@
 #### Workspace setup ####
 library(tidyverse)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+simulated_data <- read_csv("data/00-simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
+if (exists("simulated_data")) {
   message("Test Passed: The dataset was successfully loaded.")
 } else {
   stop("Test Failed: The dataset could not be loaded.")
@@ -25,64 +25,56 @@ if (exists("analysis_data")) {
 
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Check if the dataset has 10000 rows
+if (nrow(simulated_data) == 1000) {
+  message("Test Passed: The dataset has 1000 rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The dataset does not have 1000 rows.")
 }
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
+# Check if the dataset has 10 columns
+if (ncol(simulated_data) == 10) {
+  message("Test Passed: The dataset has 10 columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
-}
-
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
-} else {
-  stop("Test Failed: The 'division' column contains duplicate values.")
+  stop("Test Failed: The dataset does not have 10 columns.")
 }
 
 # Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
-                  "Western Australia", "Tasmania", "Northern Territory", 
-                  "Australian Capital Territory")
+valid_states <- c(
+  "Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
+  "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", "Idaho", 
+  "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine",
[…]

### 2024-10-31 scripts/04-test_analysis_data.R

@@ -12,28 +12,18 @@
 library(tidyverse)
 library(testthat)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+# Test that the dataset has 348 rows
+test_that("dataset has 348 rows", {
+  expect_equal(nrow(analysis_data), 348)
 })
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
-
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
-})
-
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
+# Test that the dataset has 12 columns
+test_that("dataset has 12 columns", {
+  expect_equal(ncol(analysis_data), 12)
 })
 
 # Test that the 'state' column is character type
@@ -41,29 +31,27 @@ test_that("'state' is character", {
   expect_type(analysis_data$state, "character")
 })
 
+# Test that the 'methodology' column is character type
+test_that("'methodology' is character", {
+  expect_type(analysis_data$methodology, "character")
+})
+
+# Test that the 'pollster_name' column is character type
+test_that("'pollster_name' is character", {
+  expect_type(analysis_data$pollster_name, "character")
+})
+
 # Test that there are no missing values in the dataset
 test_that("no missing values in dataset", {
   expect_true(all(!is.na(analysis_data)))
 })
 
-# Test that 'division' contains unique values (no duplicates)
-test_that("'division' column contains unique values", {
-  expect_equal(length(unique(analysis_data$division)), 151)
+# Test that there are no empty strings in 'pollster_name', 'methodology', or 'state' columns
+test_that("no empty strings in 'pollster_name', 'methodology', or 'state' columns", {
+  expect_false(any(analysis_data$pollster_name == "" | analysis_data$methodology == "" | analysis_data$state == ""))
 })
 
-# Test that 'state' contains only valid Australian state or territory names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", "Western Australia", 
[…]

### 2024-10-31 scripts/07-install_packages.R

@@ -14,5 +14,8 @@ install.packages("tidyverse")
 install.packages("arrow")
 install.packages("here")
 install.packages("kableExtra")
-install.packages("opendatatoronto")
 install.packages("janitor")
+install.packages("rstanarm")
+install.packages("usmap")
+install.packages("knitr")
+install.packages("patchwork")

### 2024-11-03 paper/paper.qmd
update model, paper, scripts

--- 2024-10-31 paper/paper.qmd
@@
 
-### Percent Support for Donald Trump
+### Percent support for Donald Trump
 The primary outcome variable is the percentage (`pct`) of respondents who indicated support for Donald Trump in the 2024 general election.
@@
 
-### Polling Methodology
+### Polling methodology
 The `methodology` variable describes the method each pollster used to collect data.
@@
             "District of Columbia"),
-  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
-                      3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
+  electoral_votes = c(9, 3, 11, 6, 54, 10, 7, 3, 30, 16, 4, 4, 19, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
+                      4, 5, 6, 4, 14, 5, 28, 16, 3, 17, 7, 8, 19, 4, 9, 3, 11, 40, 6, 3, 13, 12, 4, 10, 3, 3)
 )
@@
 
-### Polling Score and Transparency
+### Polling score and transparency
 The `numeric_grade` variable is a rating assigned to each polling organization, indicating the reliability of the poll.
@@
 
-- **Polling Scores**: Most organizations have numeric grades between 2.8 and 3.0, indicating that the majority of pollsters are considered highly reliable.
+- **Polling scores**: Most organizations have numeric grades between 2.8 and 3.0, indicating that the majority of pollsters are considered highly reliable.
 Very few have grades below 2.7, which would suggest lower reliability.
 
-- **Transparency Scores**: Transparency scores show more variability, with many pollsters achieving scores above 9, reflecting a high level of openness in their methodology.
+- **Transparency scores**: Transparency scores show more variability, with many pollsters achieving scores above 9, reflecting a high level of openness in their methodology.
 Fewer organizations have transparency scores below 6, indicating that while some pollsters are less open, the majority strive for transparency in their practices.
 
-### Sample Size
+### Sample size
 The `sample_size` variable represents the total number of respondents surveyed in each poll.
@@
 
-### Poll Duration
+### Poll duration
 The `duration` variable is a constructed variable that represents how long Donald Trump has been in the 2024 presidential campaign, measured as the number of days from his official campaign announcement on July 15, 2024 until the `end_date` of each poll.
@@
 # Model {#sec-model}
-Our modeling approach aims to quantify the relationship between various polling metrics and the percentage support for a candidate.
-For this analysis, we use a linear model (LM) to examine how factors such as poll score, methodology, poll duration, sample size, transparency score, and state influence support percentages.
-The model is implemented using the lm function, with a Gaussian distribution to capture the variability in support rates.
+
+Our modeling approach aims to quantify the relationship between various polling metrics and the percentage support for Donald Trump.
+For this analysis, we use a linear model to examine how factors such as poll score, methodology, poll duration, sample size, transparency score, and state influence support percentages.
+The model is implemented using the `stan_lm` function, with a Gaussian distribution to capture the variability in support rates.
 
@@
 This approach enables us to assess the impact of polling characteristics on candidate support while ensuring stability in our findings.
+Background details and diagnostics are included in the appendix.
+
+## Alternative model
+
+Initially, we attempted to categorize the `state` variable into two levels: state-specific polls and national polls.
+However, after modeling, we found that this approach was less effective for predicting election outcomes on a state level.
+Since the election is determined by the state-by-state electoral college, it became clear that using a state-specific variable would more accurately capture the variation needed to predict outcomes by state.
+This refinement allowed the model to better align with the electoral structure, resulting in a more accurate reflection of support distribution across states.
 
 ## Model set-up
+
 The model predicts Trump's support percentage using the following predictor variables:
 
-- Poll Score (`numeric_grade`): Represents the quality rating of the poll.
+- Poll score (`numeric_grade`): Represents the quality rating of the poll.
 
@@
 
-- Poll Duration (`duration`): The the length of the election period was conducted.
+- Poll duration (`duration`): The the length of the election period was conducted.
 
-- Sample Size (`sample_size`): The number of respondents in the poll.
+- Sample size (`sample_size`): The number of respondents in the poll.
 
-- Transparency Score (`transparency_score`): A measure of how transparent the polling data and methodology are.
+- Transparency score (`transparency_score`): A measure of how transparent the polling data and methodology are.
 
@@
     y_i \mid \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\
-    \mu_i &= \beta_0 + \beta_1 \cdot \text{Poll Score}_i + \beta_2 \cdot \text{Methodology}_i \\
-          &\quad + \beta_3 \cdot \text{Poll Duration}_i + \beta_4 \cdot \text{Sample Size}_i \\
-          &\quad + \beta_5 \cdot \text{Rransparency Score}_i + \beta_6 \cdot \text{State}_i + \epsilon_i \\
+    \mu_i &= \beta_0 + \beta_1 \cdot \text{Poll score}_i + \beta_2 \cdot \text{Methodology}_i \\
+          &\quad + \beta_3 \cdot \text{Poll duration}_i + \beta_4 \cdot \text{Sample size}_i \\
+          &\quad + \beta_5 \cdot \text{Transparency score}_i + \beta_6 \cdot \text{State}_i + \epsilon_i \\
     \epsilon_i &\sim \text{Normal}(0, \sigma^2)
@@
 ### Model justification
+
 Existing research and political science theories suggest that factors such as poll quality, sample size, transparency, methodology, poll duration, and the state where the poll takes place can influence Trump's support percentage.
 Higher quality polls and larger sample sizes are believed to yield more reliable estimates, while transparency scores can affect levels of public trust, potentially altering support.
-Moreover, different polling methodologies (e.g., online surveys, telephone interviews) may affect how representative the sample is, while longer polling durations can reflect shifts in public sentiment over time.
+Moreover, different polling methodologies (e.g., online surveys, telephone interviews) may affect how representative the sample is, while longer polling duration can reflect shifts in public sentiment over time.
 State-specific factors, such as local political events or population characteristics, can also contribute to the variation in support.
@@
 
-We predicted the outcome based on our test dataset.
-However, due to missing data for certain states in our original dataset, we were unable to make predictions for all states.
+We predicted the election outcomes based on our test dataset.
+However, due to missing data for certain states in our original dataset, predictions could not be generated for all states.
+To address this gap, we reviewed historical trends from recent elections involving Joe Biden; if a state consistently leaned toward the same candidate, we assumed this trend would continue and used it to estimate outcomes for those missing states.
 This limitation arises because the states with NA values in the dataset are not represented in the model, preventing accurate forecasts for those regions.
+Further discussion on this issue is provided in @sec-discussion.
 
-## Model Results and Interpretation
-The linear regression model built by our training dataset, using 384 data points, estimated the factors influencing Trump's support levels.
-As @tbl-summary-model shows, the intercept, estimated at 43.39, represents the level of support when all other predictors are at baseline.
-The model achieved an R-squared value of 0.85, indicating that 85% of the variance in Trump's support percentage can be explained by the predictors included in the model.
-The adjusted R-squared value of 0.82 also shows that the model effectively captures the relationships between variables without overfitting.
-The Root Mean Square Error (RMSE) was 2.03, indicating the average difference between predicted and actual values.
-The relatively low RMSE value suggests that the model provides reasonably accurate predictions.
+## Model results and interpretation
 
-The results highlight that `numeric_grade` and `sample_size` are particularly important in predicting support levels, with larger and higher-quality polls offering more reliable estimates.
-The transparency score and state-level coefficients further provide understanding into regional differences and the role of trust in polling, helping us better understand the dynamics behind Trump's public support.The coefficients for `numeric_grade` and `sample_size` underline the importance of poll quality and sample size in predicting support levels.
-Larger, higher-quality polls offer more estimates.
-Additionally, transparency and state effects provide insight into regional differences and trust factors affecting polling results, giving a clearer understanding of the dynamics influencing Trump's public support.
+The linear regression model built by our training dataset, using 242 data points, estimated the factors influencing Trump's support levels.
+For brevity, @tbl-summary-model only shows the first ten rows of the model’s coefficients, with the full model summary available in the appendix.
+The intercept is estimated at 44.224, representing the baseline support level when all predictors are at their reference levels.
+The model achieved an $R^2$ value of 0.803, indicating that 80.3% of the variance in polling outcomes is explained by the predictors included in the model.
+The adjusted $R^2$ value of 0.753 confirms that the model captures the relationships between variables without significant overfitting.
 
@@
 #| label: tbl-summary-model
-#| tbl-cap: "Summary of the Linear Regression Model for Predicting Polling Outcomes"
+#| tbl-cap: "Summary of key coefficients from the linear regression model predicting polling outcomes"
 #| echo: false
@@
 
-model2 <- readRDS(file = here::here("models/first_model.rds"))
+# Load the model
+model <- readRDS(file = here::here("models/first_model.rds"))
 
-modelsummary(
-  list(
-    "Linear Model" = model2
-  ),
-  statistic = NULL 
-)
+summary <- summary(model)
+
+summary_table <- head(summary, 10)[, 1:1]
+
+kable(col.names = c(" ", "coefficient"),
+  summary_table, digits = 3)
 ```
 
-## Predicted Electoral Outcomes
+Certain predictors have a more obvious impact than others.
+For example, `numeric_grade` (0.779) shows that a one-unit increase in grade corresponds to a 0.779 percentage point increase in predicted polling outcomes.
+The type of methodology also plays a important role: "Mixed Voting" (1.692) and "Online Ad" (0.960) methods are associated with positive effects, while "Online Panel" (-1.037) and "Probability Panel" (-1.035) methods have negative effects relative to the baseline.
+Additionally, the state-specific coefficient shows a substantial effect.
+This underlines the importance of geographic context in polling predictions, especially for politically distinct areas.
+
+Other variables, like `transparency_score` (-0.220) and `duration` (0.028), have smaller effects.
+The negative coefficient for `transparency_score` suggests a slight decrease in predicted support as transparency increases, potentially reflecting a sensitivity among the public to the transparency level in polling methods.
+Meanwhile, `sample_size` (0.002) shows a small positive effect, indicating that larger sample sizes modestly increase predicted support.
+A complete overview of all predictors is provided in the appendix.
+
+## Predicted electoral outcomes
+
 We employed a regression model to estimate the percentage of votes Trump is likely to receive in each state.
@@
 - In Arizona, Trump is expected to receive 48.94% of the vote, resulting in a win for Harris with 11 electoral votes.
-- In Missouri, Trump is projected to receive 51.64%, thereby winning all 10 electoral votes for that state.
-- In Ohio, with an estimated 51.98% of the vote, Trump secures Ohio’s 18 electoral votes.
-
-Electoral Vote Count: Trump Electoral Votes: 98 - Harris Electoral Votes: 239.
-This indicates that Harris is projected to win the 2024 U.S.
-Presidential Election with 239 electoral votes, while Trump is projected to gather 98.
-These results hinge on the outcomes in various battleground states, with several being extremely close.
+- In Texas, Trump is projected to receive 51.83%, thereby winning all 40 electoral votes for that state.
 
@@
             "District of Columbia"),
-  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
-                      3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3))
-
-# Convert methodology column to character type for recoding
-analysis_data_test$methodology <- as.character(analysis_data_test$methodology)
-
-# Recode the 'Email' level in the methodology column to 'Online Panel'
-analysis_data_test$methodology[analysis_data_test$methodology == "Email"] <- "Online Panel"
+  electoral_votes = c(9, 3, 11, 6, 54, 10, 7, 3, 30, 16, 4, 4, 19, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
+                      4, 5, 6, 4, 14, 5, 28, 16, 3, 17, 7, 8, 19, 4, 9, 3, 11, 40, 6, 3, 13, 12, 4, 10, 3, 3)
+)
 
 # Use the trained regression model to predict Trump's support percentage in each state
-analysis_data_test$predicted_percent_trump <- predict(model2, newdata = analysis_data_test)
+analysis_data_test$predicted_percent_trump <- predict(model, newdata = analysis_data_test)
 total_trump <- aggregate(predicted_percent_trump ~ state, data = analysis_data_test, FUN = mean)
@@
       col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"), 
+      digits = 2)
+```
+
+Since we are missing data for some states in our dataset, we turned to historical trends from recent elections involving Joe Biden to fill these gaps.
+For each missing state, we assessed whether it consistently leaned toward a particular candidate in past elections.
+If so, we assumed this trend would persist and used it as a basis for estimating outcomes in the current election.
+
+@tbl-history summarizes the outcomes for the missing states based on this approach.
+It shows the predicted winner for each state based on historical trend.
+For instance, Alabama, Alaska, Arkansas, Idaho, Indiana, and Iowa are expected to go to Trump, contributing their respective electoral votes to his total.
+Conversely, states like Colorado, Connecticut, Delaware, Hawaii, and Illinois are projected to favor Harris, thus allocating their electoral votes to her.
+
+```{r}
+#| label: tbl-history
+#| tbl-cap: Estimated Electoral Outcomes for Select U.S. States Based on Historical Voting Trends
+#| echo: false
+#| warning: false
+#| message: false
+
+all_states = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware",
+                        "Florida", "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky",
+                        "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
+                        "Missouri", "Montana", "Nebraska", "Nevada","New Hampshire", "New Jersey", "New Mexico", "New York",
+                        "North Carolina", "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", 
+                        "South Carolina", "South Dakota", "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", 
+                        "West Virginia", "Wisconsin", "Wyoming", "District of Columbia")
+
+uncommon_states <- setdiff(all_states, common_states)
+
+# Map the electoral votes to the uncommon states
+uncommon_states_votes <- electoral_votes %>%
+  filter(state %in% uncommon_states)
+
+missing_states <- data.frame(uncommon_states_votes,
+                             winner = c("Trump", "Trump", "Trump", "Harris", "Harris",
+                                          "Harris", "Harris", "Trump", "Harris", "Trump", "Trump",
+                                          "Trump", "Trump", "Trump", "Trump", "Trump",
+                                          "Trump", "Harris", "Trump", "Trump", "Harris", "Trump", "Trump", 
+                                          "Trump", "Trump", "Harris", "Harris", "Trump", "Trump", "Harris"))
+
+# Create and display the results table
+kable(missing_states, 
+      col.names = c("State", "Electoral Votes", "Winner"), 
       digits = 2) %>%
@@
 
-## Prediction map
+Now, we combine the results from our predicted data and the historically inferred estimates for missing states.
+This merged dataset provides a view of the expected electoral outcomes across all states.
+@tbl-final-prediction presents the final predictions, showing the estimated electoral votes and projected winner for each state based on both model predictions and historical trends.
 
 ```{r}
-#| label: fig-statemap
-#| fig-cap: Predicted Winner of 2024 US Presidential Election by State
+#| label: tbl-final-prediction
+#| tbl-cap: Final Predicted Electoral Outcomes by State, Combining Model Estimates and Historical Trends for Missing Data
 #| echo: false
@@
 
-# "red" for Trump and "blue" for Harris
-state_predictions$winner_color <- ifelse(state_predictions$winner == "Trump", "red", "blue")
+# Remove the predicted_percent_trump column from state_predictions to match missing_states
+state_predictions <- state_predictions %>%
+  select(state, electoral_votes, winner)
 
-# Create a map visualization showing the predicted winner by state
-plot_usmap(data = state_predictions, values = "winner_color", regions = "states") +
-  scale_fill_manual(values = c("red" = "red", "blue" = "blue"), name = "Predicted Winner", labels = c("Harris", "Trump")) +
-  labs(title = "Predicted Winner of the 2024 U.S. Presidential Election by State") +
-  theme(legend.position = "right")
+# Merge the two datasets
+final_predictions <- full_join(state_predictions, missing_states, by = c("state", "electoral_votes", "winner"))
 
+# Arrange the rows by state name
+final_predictions <- final_predictions %>%
+  arrange(state)
+
+# Display the final table
+kable(final_predictions, 
+      col.names = c("State", "Electoral Votes", "Winner"), 
+      digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
+  scroll_box(width = "100%", height = "400px")
 ```
-@fig-statemap displays the predicted outcome for each state in the 2024 U.S.
-Presidential Election, with green representing states where Trump is expected to win and blue for those where Harris is predicted to prevail.
 
-The map illustrates Trump gaining traction across central and southern states, including Texas and Missouri, which have traditionally leaned Republican.
-Meanwhile, Harris holds a solid lead in states along the West Coast and in the Northeast, such as California and New York, regions that have a history of Democratic support.
+## Final electoral outcomes
 
-Several battleground states, including Florida and Ohio, are projected to favor Trump, with a slight advantage that marks a contrast to Harris's stronger leads in places like California.
-The map also shows a number of central states in gray, reflecting either a lack of definitive prediction or insufficient data.
-Overall, the map reveals distinct regional patterns, with Trump expected to perform well in the heartland and Harris finding support along the coasts.
-The outcome may hinge on the final results in the competitive states like Pennsylvania, Arizona, and North Carolina.
+Based on our analysis, @tbl-final-outcome summarizes the total predicted electoral votes for Trump and Harris in the 2024 U.S.
+Presidential Election.
+In the United States, a candidate must secure at least 270 electoral votes to win the presidency.
+According to these predictions, Kamala Harris is expected to secure the majority with 341 electoral votes, while Donald Trump is projected to receive 197.
+This suggests a clear victory for Harris.
+
+```{r}
+#| label: tbl-final-outcome
+#| tbl-cap: "Predicted Final Electoral Votes for the 2024 U.S. Presidential Election: Trump vs. Harris"
+#| echo: false
+#| warning: false
+#| message: false
+
+# Calculate the electoral votes for each candidate
+final_predictions$trump_electoral_votes <- ifelse(final_predictions$winner == "Trump", final_predictions$electoral_votes, 0)
+final_predictions$harris_electoral_votes <- ifelse(final_predictions$winner == "Harris", final_predictions$electoral_votes, 0)
+
+# Summarize the total electoral votes for each candidate
+trump_electoral_votes <- sum(final_predictions$trump_electoral_votes)
+harris_electoral_votes <- sum(final_predictions$harris_electoral_votes)
+
+final_outcome <- data.frame(
+  Candidate = c("Trump", "Harris"),
+  `Final Votes` = c(trump_electoral_votes, harris_electoral_votes)
+)
+
+# Display the final table with added styling
+kable(final_outcome, col.names = c("Candidate", "Final Votes"), digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
+  row_spec(1, background = "#FFCCCC") %>%    # Add light orange background for Trump row
+  row_spec(2, background = "#C1D7FF") %>%    # Add light blue background for Harris row
+  column_spec(2, bold = TRUE)
+```
+
+```{r}
+#| label: fig-statemap
+#| fig-cap: "The predicted winner for each U.S.
+state in the 2024 presidential election based on our model.
+States shaded in blue are projected to favor Harris, while those in red are projected to favor Trump."
+#| echo: false
+#| warning: false
+#| message: false
+# Add color information based on the winner
+final_predictions <- final_predictions %>%
+  mutate(winner_color = ifelse(winner == "Trump", "#FF6F61", "#6495ED"))
+
+# Plot the map using usmap and ggplot2
+plot_usmap(data = final_predictions, values = "winner_color", regions = "states") +
+  scale_fill_identity(
+    name = "Predicted Winner",
+    labels = c("Harris", "Trump"),
+    guide = "legend"
+  ) +
+  theme_void() +
+  theme(
+    legend.position = "right",
+    legend.title = element_text(size = 10, face = "bold"),
+    legend.text = element_text(size = 18),
+    plot.background = element_rect(fill = "white", color = NA)
+  )
+```
+
+@fig-statemap displays the predicted outcome for each state in the 2024 U.S. Presidential Election, with red representing states where Trump is expected to win and blue for those favoring Harris.
+
+It shows Trump gaining support across central and southern states, including Texas and Missouri, which have traditionally leaned Republican.
+Harris, meanwhile, is projected to lead in states along the West Coast and in the Northeast, such as California and New York, regions with a history of Democratic support.
+This visual representation complements the previous electoral vote projection, where Harris is anticipated to surpass the 270-vote threshold needed to win the presidency.
 
@@
 
-## Interpretation of Polling Data and Electoral Implications
+## Interpretation of polling data and electoral implications
 
@@
 Presidential Election.
-Our linear regression model shows that poll duration and state-specific factors are the strongest predictors of Trump’s support.
-Longer poll durations tend to produce more stable data by capturing changes in public sentiment over time rather than short-term reactions.
-The state variable underscores the importance of local dynamics, as individual states bring unique policy priorities and demographic trends to their voter bases.
-These regional distinctions are essential in the Electoral College system, where state-level support directly impacts the final electoral count.
+Our linear regression model shows that numeric grade, polling methodology, and state-specific factors are key predictors of Trump’s support.
+Higher numeric grades, representing perceived poll reliability, are positively associated with Trump’s polling numbers, suggesting that well-regarded polls may capture a more favorable sentiment.
+Polling methodology also plays a significant role, with different methods (e.g., "Mixed Voting" or "Online Panel") showing varied effects on the results, likely reflecting differences in respondent engagement or accessibility.
+State-specific factors underscore the importance of regional dynamics.
+The Electoral College system makes state-level support crucial, and unique local issues and demographics in each state contribute to Trump’s polling outcomes.
 
-Transparency and sample size play secondary roles in data reliability.
-Polls with high transparency scores provide clear information about methodology, making them more reliable for analysis.
-Larger sample sizes reduce margins of error, adding stability to projections, especially in closely contested states.
-While both transparency and sample size support reliable predictions, they have less influence on voter preferences than duration and state-specific factors.
+Transparency score and sample size also affect polling reliability.
+Polls with higher transparency and larger sample sizes provide more stable projections.
+While these factors improve data quality, they have less direct influence on voter preferences than state and methodology variables.
 
-In comparison, polling methodology (e.g., live phone, online) and numeric grade (a general reliability rating) have minimal impact on Trump’s support in our model.
-Although these factors contribute to overall data quality, they do not significantly shape voter sentiment.
-This finding suggests that regional context and polling consistency over time are more important in understanding Trump’s polling performance in this election than the specific techniques or reputations of polling organizations.
+In contrast, poll duration has minimal impact in our model, suggesting that short-term and long-term polls yield similar support levels in this context.
+This finding implies that voter sentiment is more influenced by geographic and methodological context than by the length of polling periods.
+Overall, this model underscores the importance of state-level factors and methodology over specific polling practices in understanding Trump’s support trajectory in this election.
 
-## Influence of State Policies on Voter Preferences
+## Influence of state policies on voter preferences
 
-Beyond the mechanics of polling, our analysis suggests that state-specific policies and regional cultural factors could influence voter preferences and ultimately shape electoral outcomes.
-For instance, certain policies, such as the legalization of recreational marijuana, reflect broader ideological values that may correlate with support for particular candidates.
-Although our model does not directly analyze the impact of marijuana policies, including these cultural aspects could offer a more comprehensive view of voter alignment.
+Beyond the mechanics of polling, our analysis suggests that state-specific policies and regional cultural factors could influence voter preferences and eventually shape electoral outcomes, although they are not directly measured in our model.
+For example, state policies on recreational marijuana legalization may reflect broader ideological values that align with particular candidates or parties.
+To explore this idea, we compared our predictions map with a visualization of states where recreational marijuana is legal.
 
-States with legal recreational marijuana, for example, might lean more progressive or libertarian, potentially aligning with candidates like Harris who advocate for policies seen as liberal or socially progressive.
-This policy environment might signal broader state values that align with a particular party's stance, beyond just the specific candidate.
-Conversely, states that prohibit recreational marijuana use may lean more conservative, suggesting they may have stronger support for Trump.
-Although this relationship is not absolute, understanding such cultural factors helps contextualize the state-level support each candidate may receive and could be valuable in identifying battleground states.
-Additionally, factors like local economic policies, educational investment, or healthcare reform could influence voter preferences, making these areas ripe for future analysis.
+@fig-statemap-factor shows states where recreational marijuana is legal.
+Compared with @fig-statemap, many states that have legalized marijuana, such as California, Washington, and New York, also appear in our prediction as likely to support Harris, suggesting a correlation between progressive state policies and support for more liberal candidates.
+This policy environment may align with Democratic platforms on social issues, which could explain stronger support for Harris in these regions.
 
-## Limitations of the Data and Model
+In contrast, states that prohibit recreational marijuana use—many of which are predicted to lean toward Trump—might favor more conservative social policies, possibly influencing their political alignment.
+This could reflect a cultural environment that aligns more closely with Republican stances, contributing to stronger support for Trump in these areas.
 
-One limitation of this study is the incomplete dataset, with some states missing from the polling data.
-This limits our ability to produce a fully accurate prediction, as certain areas are excluded from the model.
-Additionally, the focus on state-level data may overlook finer voting patterns within states, particularly in districts with unique political identities.
+While the connection between marijuana legalization and voter preferences is not absolute, the alignment of state policies with broader political values suggests that cultural factors may influence voter preferences.
+Additionally, policies related to economic investment, healthcare, or education could shape these patterns, offering further influences into state-level political dynamics.
 
-## Future Research Directions
+```{r}
+#| label: fig-statemap-factor
+#| fig-cap: "The legal status of recreational marijuana use in each U.S. state as of 2024. States shaded in green have legalized recreational marijuana, while those in gray have not."
+#| echo: false
+#| warning: false
+#| message: false
 
-Future studies could improve by incorporating demographic variables such as age, income, and party affiliation, which might offer a clearer understanding of voter preferences.
-Examining additional state-level policies, like healthcare or education, may also provide insights into factors shaping voter choices.
+legal_marijuana_states <- c(
+  "Colorado", "Washington", "Alaska", "Oregon", "District of Columbia", "California",
+  "Maine", "Massachusetts", "Nevada", "Michigan", "Vermont", "Guam", "Illinois", 
+  "Arizona", "Montana", "New Jersey", "New York", "Virginia", "New Mexico", 
+  "Connecticut", "Rhode Island", "Maryland", "Missouri", "Delaware", "Minnesota", "Ohio"
+)
 
-Another possible enhancement involves increasing the geographic specificity of the model to include congressional districts or smaller regions, which may lead to more precise forecasts, especially in competitive states.
-As polling data collection methods evolve, combining traditional regression with machine learning techniques could allow for models that adapt to ongoing changes in public opinion, resulting in more timely and adaptable forecasts.
+all_states = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware",
+                        "Florida", "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky",
+                        "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
+                        "Missouri", "Montana", "Nebraska", "Nevada","New Hampshire", "New Jersey", "New Mexico", "New York",
+                        "North Carolina", "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", 
+                        "South Carolina", "South Dakota", "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", 
+                        "West Virginia", "Wisconsin", "Wyoming", "District of Columbia")
+
+# Create a data frame for all states with legalization status
+state_data <- data.frame(
+  state = all_states,
+  legal_marijuana = ifelse(all_states %in% legal_marijuana_states, "Legal", "Not Legal")
+)
+
+plot_usmap(data = state_data, values = "legal_marijuana") +
+  scale_fill_manual(
+    values = c("Legal" = "green", "Not Legal" = "gray"),
+    name = "Marijuana Legal Status",
+    labels = c("Legal", "Not Legal"),
+    guide = "legend"
+  ) +
+  theme_void() +
+  theme(
+    legend.position = "right",
+    legend.title = element_text(size = 10, face = "bold"),
+    legend.text = element_text(size = 8),
+    plot.background = element_rect(fill = "white", color = NA)
+  )
+```
+
+## Limitations of the data and model
+
+This paper has several limitations that affect the accuracy and breadth of its predictions.
+First, the dataset is incomplete, with some states lacking polling data.
+These omissions prevent a fully representative analysis, as the absence of data from certain regions leaves out their unique political dynamics.
+Furthermore, focusing on state-level data may obscure more localized trends, particularly in diverse districts with distinct political identities.
+For instance, urban and rural areas within the same state often show different voting patterns that a state-level analysis may overlook.
+
+Another limitation lies in the model’s emphasis on certain predictors while excluding others.
+By prioritizing variables like poll duration and sample size, we may miss factors that could better explain variations in support, such as demographic and economic data.
+Although the model performs well on a broad level, these limitations underscore the need for more nuanced data and a more inclusive approach to fully understand the range of influences on voter behavior.
+
+## Future research directions
+
+Future studies could address these limitations by including demographic variables, such as age, income, and party affiliation, to provide a clearer view of voter preferences.
+Additionally, incorporating a wider range of state-level policies, such as healthcare, education, and economic initiatives—could deepen the analysis of how local issues shape voter choices.
+Expanding the dataset in this way would allow a more detailed understanding of how social and economic factors interact with political preferences.
+
+Increasing the model’s geographic specificity to include smaller regions, such as congressional districts or precincts, could lead to more accurate forecasts, especially in closely contested states.
+This finer level of detail could capture unique district-level trends that a state-level model misses.
+Furthermore, as polling methods evolve, combining machine learning techniques with traditional regression could allow the model to adapt to shifts in public opinion, resulting in more responsive and timely predictions.
+This approach would provide a valuable foundation for tracking and forecasting voter preferences as political landscapes evolve.
 
@@
 
-# Pollster Methodology Overview and Evaluation
+# Pollster methodology overview and evaluation
 
@@
 
-## Target Population, Frame, and Sample
+## Target population, frame, and sample
 * Target Population: Registered voters or likely voters in the United States, especially voters in major battleground states during an election in 2024.
@@
 
-## Sample Recruitment
+## Sample recruitment
 The sample was recruited by telephone.
@@
 
-## Sampling Approach and Trade-offs
+## Sampling approach and trade-offs
 Siena/NYT used a stratified sampling method [@citeNYT].
@@
 
-## Non-response Handling
+## Non-response handling
 
@@
 
-## Questionnaire Evaluation
+## Questionnaire evaluation
 
@@
 
-# Idealized Methodology and Survey
+# Idealized methodology and survey
 
@@
 
-## Sampling Approach
+## Sampling approach
 The sampling approach is designed to increase coverage and ensure that a representative voting population is covered.
@@
 
-### Stratification Variables 
+### Stratification variables 
 * Age: 18-29, 30-44, 45-64, 65+
 * Gender: Male, Female, Non-binary
-* Race: White, Black /African American, Hispanic/Latino, Asian, Native, Other
+* Race: White, Black/African American, Hispanic/Latino, Asian, Native, Other
 * Education level: High School, Some College, Bachelor's Degree, Graduate Degree, Other
@@
 
-### Sample Size
+### Sample size
 The target sample size was 5,000 respondents, which are stratified by the Stratification Variables described above.
@@
 
-## Recruitment Strategy
+## Recruitment strategy
 The recruitment strategy was separated into two main approaches to ensure a diverse and representative sample:
 
-**Online Survey panels:**
+**Online survey panels:**
 
@@
 
-**Social Media Advertising:**
+**Social media advertising:**
 
@@
 
-* **Attention Checks:** At least two 'attention check' questions will be included in the survey to identify inattention or robots.
-* **Duplicate Detection:** Use email or IP-based verification to prevent duplicate responses. Ensure that each respondent provides only one response set to keep the dataset unique.
-* **Response Time Monitoring:** Track the time it takes respondents to complete surveys. Responses with apparently faster-than-average completion times are labelled as potentially low-quality.
-* **Data Consistency Check:** Analyses the consistency of responses, especially between related questions. Inconsistent answers will be labelled for review.
+* **Attention checks:** At least two 'attention check' questions will be included in the survey to identify inattention or robots.
+* **Duplicate detection:** Use email or IP-based verification to prevent duplicate responses. Ensure that each respondent provides only one response set to keep the dataset unique.
+* **Response time monitoring:** Track the time it takes respondents to complete surveys. Responses with apparently faster-than-average completion times are labelled as potentially low-quality.
+* **Data consistency check:** Analyses the consistency of responses, especially between related questions. Inconsistent answers will be labelled for review.
 * **Panel partner validation:** For respondents recruited through an online survey panel, rely on the panel provider's in-built validation systems.
@@
 ## Poll aggregation and forecasting
+
 ### Poll aggregation
@@
 
-### Forecasting Method
+### Forecasting method
 * Bayesian modelling: Aggregate polling data is combined with historical electoral trends and demographic information using Bayesian statistical models.
@@
 
-## Budget Allocation
+## Budget allocation
 * Survey Panel Recruitment: $50,000
@@
 
-## Survey Implementation
+## Survey implementation
 The survey will be available via Google Forms to ensure broad accessibility and easy data collection.
@@
 
-**Distribution Plan:**
+**Distribution plan:**
 
@@
 
-## Survey Structure
+## Survey structure
 
-**Survey Introduction:**
+**Survey introduction:**
 Welcome!
@@
 
-**Survey Question:**
+**Survey question:**
 
@@
 
-**Part 3: Voting Intentions**
+**Part 3: Voting intentions**
 
@@
 
-**Part 4: Information Sources and Engagement**
+**Part 4: Information sources and engagement**
 
@@
 
-# Model details 
+# Data manipulation and cleaning {#sec-data-cleaning}
+
+In the data cleaning process, we prepared the raw election data for analysis by applying transformations, filtering, and restructuring using several R packages, including `dplyr` [@citedplyr], `janitor` [@citejanitor], `tidyverse` [@citetidyverse], `arrow` [@citearrow], and `rsample` [@citersample].
+
+1. **Standardizing column names**: Using the `clean_names()` function, we converted column names to a consistent lowercase format, making them easier to reference and manipulate.
+
+2.
+**Filtering polls by quality and candidate**: With the `dplyr` package from `tidyverse`, we filtered the dataset to include only higher-quality polls with a `numeric_grade` of 2.5 or above, ensuring that only credible polls were considered.
+We further filtered to focus on polls related specifically to Donald Trump (`candidate_name == "Donald Trump"`), aligning the dataset with our analysis objective.
+
+3.
+**Date conversion and filtering**: We converted the `end_date` column to a Date format using `mdy()` from `lubridate` (part of `tidyverse`), ensuring date consistency.
+We then filtered the data to include only polls conducted after July 15, 2024—the date of Trump’s campaign announcement—allowing us to focus on his active campaign period.
+
+4. **Creating duration and support columns**:
+   - **Duration**: We created a `duration` variable using the `difftime()` function from base `R`, which calculates the number of days between each poll’s end date and Trump’s campaign start date.
+This allows us to observe how polling data shifts over time.
+   - **Number of Trump supporters**: We calculated `num_trump`, the estimated number of respondents supporting Trump in each poll, by applying the support percentage (`pct`) to the sample size and rounding the result with `dplyr` functions.
+
+5.
+**Methodology update**: We used `str_detect()` from `stringr` (in `tidyverse`) to identify polls that listed multiple polling methods (e.g., those containing “/”) and standardized them to "Mixed Voting" to clarify the `methodology` column.
+
+6.
+**Selecting and renaming columns**: We used `dplyr` functions to select the relevant columns (`poll_id`, `numeric_grade`, `methodology`, `transparency_score`, `end_date`, `sample_size`, `pollster_name` (renamed from `display_name`), `state`, `pct`, `duration`, and `num_trump`), streamlining the dataset for analysis.
+
+7.
+**Removing duplicates and missing values**: With `dplyr`, we removed duplicate rows using `distinct()` and dropped rows with missing values using `drop_na()`, ensuring that only complete and unique data entries were retained.
+
+8.
+**Splitting the data**: We utilized `rsample` to perform a stratified split on the cleaned dataset, using the `state` variable to ensure balanced representation across states.
+The data was divided into training (70%) and testing (30%) sets, preparing it for modeling.
+
+Finally, we saved the cleaned dataset and the training/testing splits in CSV and Parquet formats using `arrow`, facilitating efficient storage and future accessibility.
+
+# Model details {sec-model-details}
 ```{r}
@@
 
-# Generate diagnostic plots for model2
-par(mfrow = c(2, 2))
-plot(model2)
-
-# Generate pairwise scatter plots for all predictor variables
-pairs(analysis_data_train[, c("numeric_grade", "duration", "sample_size", "transparency_score")])
 ```

### 2024-11-03 scripts/03-clean_data.R

@@ -16,29 +16,32 @@ library(tidyverse)
 #### Clean data ####
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 
-legal_marijuana_states <- c(
-  "Colorado", "Washington", "Alaska", "Oregon", "Washington, D.C.", "California",
-  "Maine", "Massachusetts", "Nevada", "Michigan", "Vermont", "Guam", "Illinois", 
-  "Arizona", "Montana", "New Jersey", "New York", "Virginia", "New Mexico", 
-  "Connecticut", "Rhode Island", "Maryland", "Missouri", "Delaware", "Minnesota", "Ohio"
-)
-
 cleaned_data <- 
   raw_data |> 
   janitor::clean_names() |> 
   filter(numeric_grade >= 2.5, candidate_name == "Donald Trump") |> 
-  mutate(end_date = mdy(end_date)) |>
+  mutate(
+    end_date = mdy(end_date),
+    state = case_when(              # Aggregate sub-regions into main states
+      state %in% c("Nebraska", "Nebraska CD-2") ~ "Nebraska",
+      state %in% c("Maine", "Maine CD-1", "Maine CD-2") ~ "Maine",
+      TRUE ~ state
+    )
+  ) |>
   filter(end_date >= as.Date("2024-07-15")) |>  # Trump announced joining campaign
   mutate(
     duration = as.numeric(difftime(end_date, min(end_date), units = "days")),  # New column: duration (end_date - start_date of Trump)
     num_trump = round((pct / 100) * sample_size, 0),  # Number of respondents supporting Trump
-    methodology = ifelse(str_detect(methodology, "/"), "Mixed Voting", methodology),  # Replace "/" with "multiple ways of voting"
-    marijuana_legal = ifelse(state %in% legal_marijuana_states, 1, 0)  # Map whether the state allows marijuana legally
-  ) |> 
+    methodology = case_when(
+      str_detect(methodology, "/") ~ "Mixed Voting",
+      methodology == "Email" ~ "Online Panel",   # Aggregate Email to Online Panel
+      methodology == "IVR" ~ "Live Phone",        # Aggregate IVR to Live Phone
+      TRUE ~ methodology
+    )) |> 
   select(
     poll_id, numeric_grade, methodology, transparency_score, 
-    end_date, sample_size, pollster_name = display_name,  # Rename display_name to pollster_name
-    state, pct, duration, num_trump, marijuana_legal
[…]

### 2024-11-03 scripts/06-model_data.R

@@ -17,33 +17,24 @@ library(car)
 library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
-analysis_data_test <- read_parquet("data/02-analysis_data/test_data.parquet")
 analysis_data_train <- read_parquet("data/02-analysis_data/train_data.parquet")
 
 
 ### Model data ####
-first_model <-
+model <-
   stan_glm(
-    formula = pct~ numeric_grade + as.factor(methodology) + duration + transparency_score + state,
+    formula = pct ~ numeric_grade + as.factor(methodology) + duration + sample_size + transparency_score + state,
     data = analysis_data_train,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
-  )
-summary(first_model)
-vif(first_model)
-
-model2 <-lm(pct~ numeric_grade + as.factor(methodology) + duration + sample_size + transparency_score + state, 
-            data = analysis_data_train)
-summary(model2)
-vif(model2)
+)
 
 
 #### Save model ####
 saveRDS(
-  model2,
+  model,
   file = "models/first_model.rds"
 )

### 2024-11-03 paper/paper.qmd
update Appendix B

@@
 * Race: White, Black/African American, Hispanic/Latino, Asian, Native, Other
+* Income Level: <$30,000,  \$30,000-\$59,999, \$60,000-\$99,999, >\$100,000
 * Education level: High School, Some College, Bachelor's Degree, Graduate Degree, Other
@@
 * Male / Female / Non-binary / Prefer not to say\
-6.Which of the following best describes your education level?\
-* High School / Some College / Bachelor's Degree / Graduate Degree / Other\
-7.Which region of the U.S. do you currently reside in?\
+6.Which of the following best describes your race or ethnicity?
+* White / Black / African American / Hispanic or Latino / Asian / Native / Other\
+7.Which of the following best describes your education level?\
+* High School / Some College / Bachelor's Degree / Graduate Degree / Prefer not to say/ Other\
+8.What was your family/individual income last year?
+* <$30,000 / \$30,000-\$59,999 / \$60,000-\$99,999 / >\$100,000 / Prefer not to say\
+9.Which region of the U.S. do you currently reside in?\
 * Northeast / Midwest / South / West\    
-8.Do you generally identify with a political party?\
-* Democratic / Republican / Independent / None
+10.Do you generally identify with a political party?\
+* Democratic / Republican / Independent / None / Prefer not to say
 
@@
 
-9.How likely are you to participate in the upcoming presidential election?\
+11.How likely are you to participate in the upcoming presidential election?\
 * Very Likely / Somewhat Likely / Not Sure / Unlikely / Very Unlikely\
-10.If the presidential election were held today, for which candidate would you vote?\
+12.If the presidential election were held today, for which candidate would you vote?\
 * Kamala Harris (Democrat) / Donald Trump (Republican) / Undecided / Prefer not to say\
-11.What are the top three issues that will influence your vote?\
+13.What are the top three issues that will influence your vote?\
 * Economy / Healthcare / Education / Gun Policy / Taxes / Foreign Policy / Social Security / Civil Rights / Technology / Privacy / Other[text]
@@
 
-12.Which of the following sources do you rely on most for political news and information?\
+14.Which of the following sources do you rely on most for political news and information?\
 * Television News / Newspapers / Online News Websites / Social Media / Radio / Friends and Family / Other\
-13.How often do you engage in discussions about political topics with friends or family?\
+15.How often do you engage in discussions about political topics with friends or family?\
 * Daily / Weekly / Monthly / Rarely / Never
@@
 
-14.Please select 'Agree' to verify that you are paying attention.\
+16.Please select 'Agree' to verify that you are paying attention.\
 * Agree / Disagree\
-15.Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.\
+17.Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.\
 * Yes / No

### 2024-11-03 paper/paper.qmd
update abstract and introduction

@@
 abstract: "In this paper, we develop a linear model to predict the outcome of the 2024 U.S.
-presidential election using a \"poll-of-polls\" approach that combines data from various prominent pollsters.
-Our analysis indicates that Donald Trump’s probability of winning varies between 45% and 55% across states, depending on regional polling trends.
-However, Kamala Harris is projected to secure key states and achieve a majority of electoral votes, with a projected count of 239 to Trump’s 98 based on the testing dataset.
+presidential election using a \"poll-of-polls\" approach that aggregates data from multiple well-known pollsters.
+Our analysis projects that Donald Trump's probability of winning ranges from 30% to 52%, which depends on regional polling trends.
+However, Kamala Harris is projected to secure key states and obtain the majority of electoral votes, with a predicted count of 341 to Trump's 197 based on the testing dataset.
 These predictions are based on the testing dataset, which lacks data for some states, limiting our ability to produce results for all states.
-This paper underscore the effectiveness of aggregated polls in producing reliable election forecasts."
+This paper underscores the effectiveness of aggregated polls in producing reliable election forecasts."
 format: pdf
@@
 
+In this study, our estimand is Donald Trump's percentage of polling in each state ahead of the 2024 U.S.
+presidential election.
+The object of the estimation is Trump's percentage of polling data in each state based on aggregated information from various sources.
+By using a linear regression model, we aim to capture changes in public opinion over time and provide a clearer understanding of voter preferences and the likely election outcome.
+
 Our findings suggest that while Trump has a competitive chance, Harris is projected to win key states and receive a majority of electoral votes.
-Harris will receive 239 electoral votes to Trump's 98 votes.
+Harris is estimated to receive 341 electoral votes to Trump's 197, and the uncertainty around these estimates is represented by confidence intervals, which take into account polling changes and model assumptions.
 This is important because accurate election forecasts help reduce uncertainty, which allows political stakeholders to allocate resources efficiently and gives the public a better understanding of likely outcomes.
@@
 Eventually, @sec-discussion concludes with a discussion of the findings, evaluating the reliability of the forecasts and identifying potential limitations of the models.
-
-## Estimand
-
-In this study, our estimand is Donald Trump's percentage of polling in each state ahead of the 2024 U.S.
-presidential election.
-The object of the estimation is Trump's percentage of polling data in each state based on aggregated information from various sources By using a linear regression model, we aim to capture changes in public opinion over time and provide a clearer understanding of voter preferences and the likely election outcome.
 

### 2024-11-04 paper/paper.qmd
update readme, finalize paper, fix reference

@@
 title: "Predicting the 2024 US Presidential Election with a Model-Based Forecast"
-subtitle: "Using Generalized Linear Models to Predict Election Outcomes"
+subtitle: "Kamala Harris Predicted to Lead with 341 Electoral Votes Based on a Poll-Based Prediction"
 author: 
@@
 presidential election using a \"poll-of-polls\" approach that aggregates data from multiple well-known pollsters.
-Our analysis projects that Donald Trump's probability of winning ranges from 30% to 52%, which depends on regional polling trends.
-However, Kamala Harris is projected to secure key states and obtain the majority of electoral votes, with a predicted count of 341 to Trump's 197 based on the testing dataset.
-These predictions are based on the testing dataset, which lacks data for some states, limiting our ability to produce results for all states.
-This paper underscores the effectiveness of aggregated polls in producing reliable election forecasts."
+By analyzing state-level polling trends, our model predicts that Kamala Harris is likely to secure key states, leading to an estimated electoral vote count of 341 for Harris and 197 for Donald Trump.
+This approach, which combines multiple polls, reduces bias and improves reliability, providing a more accurate picture of public sentiment leading up to the election."
 format: pdf
@@
 @sec-model introduces the forecasting models, explaining why the selected models are suitable for predicting election outcomes based on aggregated polling data.
-Then @sec-result presents the main findings, including detailed crime trends for each neighborhood and year.
-Finally, @sec-discussion provides the results, highlighting key trends and predictions.
+Then, @sec-result provides the results, highlighting key trends and predictions.
 Eventually, @sec-discussion concludes with a discussion of the findings, evaluating the reliability of the forecasts and identifying potential limitations of the models.
@@
 ggplot(cleaned_data, aes(x = end_date, y = pct)) +
-  geom_point() +  # Add points for individual poll data
+  geom_point(alpha = 0.5) +  # Add points for individual poll data
   scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") +  # Show month and year, with one label per month
@@
 
-@fig-trump-pct shows Donald Trump's polling percentages over time from July to October 2024.
+Using package `ggplot2` [@citeggplot], @fig-trump-pct shows Donald Trump's polling percentages over time from July to October 2024.
 Each black dot represents an individual poll conducted on a specific date, indicating the percentage of voters who supported Trump in that poll.
@@
 The methodology is important because different approaches can introduce varying degrees of bias, influencing the final reported percentages.
-
-Placeholder for a table showing the distribution of polling methodologies across different states.
 
@@
 This approach enables us to assess the impact of polling characteristics on candidate support while ensuring stability in our findings.
-Background details and diagnostics are included in the appendix.
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 The linear regression model built by our training dataset, using 242 data points, estimated the factors influencing Trump's support levels.
-For brevity, @tbl-summary-model only shows the first ten rows of the model’s coefficients, with the full model summary available in the appendix.
+For brevity, @tbl-summary-model only shows the first ten rows of the model’s coefficients, with the full model summary available in [Appendix -@sec-model-details].
 The intercept is estimated at 44.224, representing the baseline support level when all predictors are at their reference levels.
@@
 Meanwhile, `sample_size` (0.002) shows a small positive effect, indicating that larger sample sizes modestly increase predicted support.
-A complete overview of all predictors is provided in the appendix.
+A complete overview of all predictors is provided in [Appendix -@sec-model-details].
 
@@
       col.names = c("State", "Electoral Votes", "Winner"), 
-      digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
-  scroll_box(width = "100%", height = "400px")
-```
-
-Now, we combine the results from our predicted data and the historically inferred estimates for missing states.
-This merged dataset provides a view of the expected electoral outcomes across all states.
-@tbl-final-prediction presents the final predictions, showing the estimated electoral votes and projected winner for each state based on both model predictions and historical trends.
-
-```{r}
-#| label: tbl-final-prediction
-#| tbl-cap: Final Predicted Electoral Outcomes by State, Combining Model Estimates and Historical Trends for Missing Data
-#| echo: false
-#| warning: false
-#| message: false
-
-# Remove the predicted_percent_trump column from state_predictions to match missing_states
-state_predictions <- state_predictions %>%
-  select(state, electoral_votes, winner)
-
-# Merge the two datasets
-final_predictions <- full_join(state_predictions, missing_states, by = c("state", "electoral_votes", "winner"))
-
-# Arrange the rows by state name
-final_predictions <- final_predictions %>%
-  arrange(state)
-
-# Display the final table
-kable(final_predictions, 
-      col.names = c("State", "Electoral Votes", "Winner"), 
-      digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
-  scroll_box(width = "100%", height = "400px")
+      digits = 2)
 ```
@@
 
+state_predictions <- state_predictions %>%
+  select(state, electoral_votes, winner)
+
+final_predictions <- full_join(state_predictions, missing_states, by = c("state", "electoral_votes", "winner"))
+
 # Calculate the electoral votes for each candidate
@@
 kable(final_outcome, col.names = c("Candidate", "Final Votes"), digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
   row_spec(1, background = "#FFCCCC") %>%    # Add light orange background for Trump row
@@
     legend.title = element_text(size = 10, face = "bold"),
-    legend.text = element_text(size = 18),
+    legend.text = element_text(size = 8),
     plot.background = element_rect(fill = "white", color = NA)
@@
 
-@fig-statemap displays the predicted outcome for each state in the 2024 U.S. Presidential Election, with red representing states where Trump is expected to win and blue for those favoring Harris.
+By using package `usmap` [@citeusmap], @fig-statemap displays the predicted outcome for each state in the 2024 U.S.
+Presidential Election, with red representing states where Trump is expected to win and blue for those favoring Harris.
 
@@
 
-# Model details {sec-model-details}
+# Model details {#sec-model-details}
+
+## Model summary
+
+@tbl-summary presents the coefficients from our model analyzing factors that influence polling outcomes.
+The intercept value, 44.178, represents the baseline level of support when all other predictors are at their reference or baseline levels.
+Key variables include "numeric_grade," with a positive coefficient indicating that higher grades correlate with increased support.
+Different polling methodologies show varying effects; for example, "Mixed Voting" has a positive coefficient of 1.697, while "Online Panel" and "Probability Panel" methods have negative coefficients, suggesting that these methods might be associated with lower support levels in polling outcomes.
+
 ```{r}
-#| label: fig-qq-check
-#| fig-cap: Model Diagnosis
+#| label: tbl-summary
+#| tbl-cap: "Coefficients from a regression model examining factors influencing polling outcomes, including polling methodology, duration, transparency, and state-level indicators."
 #| echo: false
 #| warning: false
+
+modelsummary(
+  list(
+    "coefficient" = model
+  )
+)
+```
+
+## Posterior predictive check
+
+In @fig-ppcheck, we implement a posterior predictive check, which displays the overlap between the observed data (denoted by $y$) and the replicated data generated from the model (denoted by $y_{rep}$).
+In a well-fitting model, the distribution of these replicated data should resemble the distribution of the observed data.
+Here, the replicated lines closely follow the shape and central tendency of the observed data’s density, especially around the peak.
+This similarity indicates that the model is capturing the overall pattern of the data reasonably well, suggesting a good fit.
+Deviations between the replicated and observed lines would indicate areas where the model might not be accurately capturing the data structure.
+
+```{r}
+#| eval: true
+#| echo: false
 #| message: false
+#| warning: false
+#| label: fig-ppcheck
+#| fig-cap: "Comparison of Observed Data Density (dark line) and Model-Generated Replications (light lines) shows close alignment, suggesting the model captures the main distributional characteristics of the data."
 
+pp_check(model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
 ```
+
+## Diagnostics
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-rhat
+#| fig-cap: "All parameters have R-hat values at or below 1.05, indicating strong convergence of the MCMC chains and reliable parameter estimates."
+
+plot(model, "rhat")
+```
+
+@fig-rhat is a visualization of the Gelman-Rubin diagnostic, often denoted as R-hat, which assesses the convergence of a Bayesian model’s Markov Chain Monte Carlo (MCMC) samples.
+It shows the values of for various parameters in the model.
+An value close to 1 indicates good convergence, meaning the chains for each parameter have mixed well and are sampling from the same posterior distribution.
+In @fig-rhat, all parameters have an value at or below 1.05, suggesting that the model has achieved adequate convergence and the estimates are reliable.
 

### 2024-11-04 paper/paper.qmd
finalize paper and update scripts

@@
 The model achieved an $R^2$ value of 0.803, indicating that 80.3% of the variance in polling outcomes is explained by the predictors included in the model.
-The adjusted $R^2$ value of 0.753 confirms that the model captures the relationships between variables without significant overfitting.
+The adjusted $R^2$ value of 0.753 confirms that the model captures the relationships between variables without overfitting.
 
@@
 # Load the model
-model <- readRDS(file = here::here("models/first_model.rds"))
+model <- readRDS(file = here::here("models/linear_model.rds"))
 
@@
 
-Since we are missing data for some states in our dataset, we turned to historical trends from recent elections involving Joe Biden to fill these gaps.
+Since we are missing data for some states in our dataset, we turned to historical trends from recent elections involving Joe Biden to fill these blanks.
 For each missing state, we assessed whether it consistently leaned toward a particular candidate in past elections.
@@
 Higher numeric grades, representing perceived poll reliability, are positively associated with Trump’s polling numbers, suggesting that well-regarded polls may capture a more favorable sentiment.
-Polling methodology also plays a significant role, with different methods (e.g., "Mixed Voting" or "Online Panel") showing varied effects on the results, likely reflecting differences in respondent engagement or accessibility.
+Polling methodology also plays an important role, with different methods (e.g., "Mixed Voting" or "Online Panel") showing varied effects on the results, likely reflecting differences in respondent engagement or accessibility.
 State-specific factors underscore the importance of regional dynamics.
-The Electoral College system makes state-level support crucial, and unique local issues and demographics in each state contribute to Trump’s polling outcomes.
+The Electoral College system makes state-level support essential, and unique local issues and demographics in each state contribute to Trump’s polling outcomes.
 
@@
 For example, state policies on recreational marijuana legalization may reflect broader ideological values that align with particular candidates or parties.
-To explore this idea, we compared our predictions map with a visualization of states where recreational marijuana is legal.
+To examine this further, we compared our predictions map with a visualization of states where recreational marijuana is legal.
 
@@
 By prioritizing variables like poll duration and sample size, we may miss factors that could better explain variations in support, such as demographic and economic data.
-Although the model performs well on a broad level, these limitations underscore the need for more nuanced data and a more inclusive approach to fully understand the range of influences on voter behavior.
+Although the model performs well on a broad level, these limitations underscore the need for a more inclusive approach to fully understand the range of influences on voter behavior.
 

### 2024-11-04 scripts/00-simulate_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of 2024 US election, to explore what plausible values might appear in the dataset.
+# Purpose: Simulates a dataset of 2024 US election to explore what values might appear in the dataset.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
@@ -14,154 +14,56 @@ set.seed(853)
 
 
 #### Simulate data ####
-#determine the number of observations
+# Define the number of observations
 num_obs <- 1000
 
-#pollster names
-pollster <- c(
-  "The New York Times/Siena College", 
-  "ABC News/The Washington Post", 
-  "Marquette University Law School", "YouGov",
-  "Monmouth University Polling Institute", 
-  "Marist College", "Suffolk University","Data Orbital", 
-  "University of Massachusetts Lowell Center for Public Opinion", 
-  "Emerson College", 
-  "Muhlenberg College Institute of Public Opinion", 
-  "Selzer & Co.", 
-  "University of North Florida Public Opinion Research Lab", 
-  "CNN","SurveyUSA", "Beacon Research/Shaw & Co. Research", 
-  "Quinnipiac University", "MassINC Polling Group", "Ipsos", 
-  "Christopher Newport University Wason Center for Civic Leadership", 
-  "Siena College","AtlasIntel", "Echelon Insights", 
-  "The Washington Post/George Mason University Schar School of Policy and Government", 
-  "East Carolina University Center for Survey Research", 
-  "Data for Progress", 
-  "Hart Research Associates/Public Opinion Strategies",
-  "University of New Hampshire Survey Center", 
-  "Stockton University William J. Hughes Center for Public Policy", 
-  "Remington Research Group", 
-  "Mason-Dixon Polling & Strategy",
-  "Roanoke College Institute for Policy and Opinion Research", 
-  "Fairleigh Dickinson University", 
-  "University of Arkansas Department of Political Science", 
-  "Lake Research Partners/The Tarrance Group",
-  "Public Policy Institute of California", 
-  "Michigan State University Institute for Public Policy and Social Research",
-  "Elon University", 
[…]

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -5,76 +5,90 @@
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
+#   - The `tidyverse`, `testthat` packages must be installed and loaded
+#   - 00-simulate_data.R must have been run
 # Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(testthat)
 
 simulated_data <- read_csv("data/00-simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
-if (exists("simulated_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
+test_that("dataset was successfully loaded", {
+  expect_true(exists("simulated_data"))
+})
 
 
 #### Test data ####
 
-# Check if the dataset has 10000 rows
-if (nrow(simulated_data) == 1000) {
-  message("Test Passed: The dataset has 1000 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 1000 rows.")
-}
+# Check if the dataset has 1000 rows
+test_that("dataset has 1000 rows", {
+  expect_equal(nrow(simulated_data), 1000)
+})
 
-# Check if the dataset has 10 columns
-if (ncol(simulated_data) == 10) {
-  message("Test Passed: The dataset has 10 columns.")
-} else {
-  stop("Test Failed: The dataset does not have 10 columns.")
-}
+# Check if the dataset has 11 columns
+test_that("dataset has 11 columns", {
+  expect_equal(ncol(simulated_data), 11)
+})
 
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c(
-  "Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
-  "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", "Idaho", 
-  "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine",
-  "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
[…]

### 2024-11-04 scripts/02-download_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from FiveThirtyEight
+# Purpose: Downloads and saves the data from FiveThirtyEight.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: None
-# Any other information needed? None
+# Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Workspace setup ####

### 2024-11-04 scripts/03-clean_data.R

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: Cleans the raw election data
+# Purpose: Cleans the raw election data.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: None
-# Any other information needed? None
+# Pre-requisites: 
+#   - The `tidyverse`, `arrow`, `rsample` packages must be installed and loaded
+#   - 02-download_data.R must have been run
+# Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Workspace setup ####

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: Tests structure of the analysis data 
+# Purpose: Tests structure of the analysis data.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: None
-# Any other information needed? None
+# Pre-requisites: 
+#   - The `tidyverse`, `testthat` packages must be installed and loaded
+#   - 03-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Workspace setup ####
@@ -21,9 +23,9 @@ test_that("dataset has 348 rows", {
   expect_equal(nrow(analysis_data), 348)
 })
 
-# Test that the dataset has 12 columns
-test_that("dataset has 12 columns", {
-  expect_equal(ncol(analysis_data), 12)
+# Test that the dataset has 11 columns
+test_that("dataset has 11 columns", {
+  expect_equal(ncol(analysis_data), 11)
 })
 
 # Test that the 'state' column is character type
@@ -54,4 +56,48 @@ test_that("no empty strings in 'pollster_name', 'methodology', or 'state' column
 # Test that the 'methodology' column contains at least 3 unique values
 test_that("'methodology' column contains at least 3 unique values", {
   expect_true(length(unique(analysis_data$methodology)) >= 3)
+})
+
+# Test that the 'state' column contains only valid US state names
+valid_states <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware",
+                  "Florida", "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky",
+                  "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
+                  "Missouri", "Montana", "Nebraska", "Nevada","New Hampshire", "New Jersey", "New Mexico", "New York",
+                  "North Carolina", "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", 
+                  "South Carolina", "South Dakota", "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", 
[…]

### 2024-11-04 scripts/05-exploratory_data_analysis.R

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: Models US presidential election polls by using LM 
+# Purpose: Exploratory data analyis on cleaned data.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: None
-# Any other information needed? None
+# Pre-requisites: 
+#   - The `tidyverse`, `rstanarm` packages must be installed and loaded
+#   - 03-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Workspace setup ####
@@ -15,33 +17,97 @@ library(rstanarm)
 #### Read data ####
 analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
-numeric_vars_analysis <- c('numeric_grade', 'transparency_score', 'sample_size', 'pct')
-for (var in numeric_vars_analysis) {
-  p1 <- ggplot(analysis_data, aes(x = !!sym(var))) +
-    geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) +
-    ggtitle(paste("Histogram of", var)) +
-    theme_minimal() +
-    xlab(var) +
-    ylab("Frequency")
-  print(p1) 
-}
+# General overview of the dataset
+glimpse(analysis_data)
+summary(analysis_data)
 
 
-numeric_vars_electoral <- c('duration', 'num_trump')
-for (var in numeric_vars_electoral) {
-  p <- ggplot(electoral_votes, aes(x = !!sym(var))) +
-    geom_histogram(binwidth = 5, fill = "lightgreen", color = "black", alpha = 0.7) +
-    ggtitle(paste("Histogram of", var)) +
-    theme_minimal() +
-    xlab(var) +
-    ylab("Frequency")
-  print(p)  
-}
+#### Summary Statistics ####
+# Summary of numeric columns
+analysis_data %>%
+  select_if(is.numeric) %>%
+  summary()
 
-p_numeric_grade <- ggplot(analysis_data, aes(x = numeric_grade)) +
-  geom_bar(fill = "coral", color = "black", alpha = 0.8) +
[…]

### 2024-11-04 scripts/06-model_data.R

@@ -1,18 +1,18 @@
 #### Preamble ####
-# Purpose: Models US presidential election polls by using LM, and compare two regression models
+# Purpose: Models US presidential election polls by using stan_glm.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: None
-# Any other information needed? None
+# Pre-requisites: 
+#   - The `tidyverse`, `rstanarm`, `arrow`, `car` packages must be installed and loaded
+#   - 03-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
-library(rsample)
-library(dplyr)
 library(car)
 library(arrow)
 
@@ -36,5 +36,5 @@ model <-
 #### Save model ####
 saveRDS(
   model,
-  file = "models/first_model.rds"
+  file = "models/linear_model.rds"
 )

### 2024-11-04 scripts/07-install_packages.R

@@ -1,12 +1,11 @@
 #### Preamble ####
-# Purpose: Install necessary packages
+# Purpose: Install necessary packages.
 # Author: Yuanyi (Leo) Liu, Dezhen Chen, Ziyuan Shen
 # Date: 30 October 2024
 # Contact: leoy.liu@mail.utoronto.ca, dezhen.chen@mail.utoronto.ca, ziyuan.shen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: None
-# Any other information needed? None
-
+# Any other information needed? Make sure you are in the `Forecasting-the-2024-US-Presidential-Election` rproj
 
 
 #### Install packages ####
@@ -19,3 +18,9 @@ install.packages("rstanarm")
 install.packages("usmap")
 install.packages("knitr")
 install.packages("patchwork")
+install.packages("car")
+install.packages("testthat")
+install.packages("rsample")
+install.packages("ggplot2")
+install.packages("modelsummary")
+install.packages("usmap")

### 2024-11-04 paper/paper.qmd
update appendix

@@
 * Target Population: Registered voters or likely voters in the United States, especially voters in major battleground states during an election in 2024.
-* Sample Frame: U.S. registered voters based on a national voter file maintained by L2, with a cell phone number that matches the voter file.
+* Sample Frame: U.S.
+registered voters from a national voter file maintained by L2, a nonpartisan provider of detailed voter data, including demographics and voting history.
+The sample includes voters with matching cell phone numbers.
 * Sample Size: Sample sizes vary across different polls.

### 2024-11-04 paper/paper.qmd
update Appendix B survey part

@@
 **Survey introduction:**
+
 Welcome!
+
 We are surveying to better understand voter preferences and priorities for the upcoming U.S.
@@
 Your participation is important and your answers will help us accurately predict the outcome of the election.
-It will take approximately 10 minutes to complete the survey.
-All responses are confidential and will be used for research purposes only.
+
+Please note:
+
+* All responses are confidential and will be used for research purposes only.
+* This survey will take approximately 10 minutes to complete.
+* Your participation is entirely voluntary, and you may withdraw at any time.
+* All questions marked with an asterisk () are required.*
+* There are no right or wrong answers, we appreciate your honest opinions.
 

### 2024-11-04 paper/paper.qmd
fix git

@@
   geom_bar(fill = "steelblue", color = "black") +
-  labs(title = "Distribution of Polling Scores",
-       x = "Numeric Grade",
+  labs(x = "Numeric Grade",
        y = "Count") +
@@
   geom_bar(fill = "darkorange", color = "black") +
-  labs(title = "Distribution of Transparency Scores",
-       x = "Transparency Score",
+  labs(x = "Transparency Score",
        y = "Count") +

### 2024-11-04 paper/paper.qmd
finalize paper

@@
 abstract: "In this paper, we develop a linear model to predict the outcome of the 2024 U.S.
-presidential election using a \"poll-of-polls\" approach that aggregates data from multiple well-known pollsters.
+presidential election using a \"poll-of-polls\" approach that aggregates data from multiple pollsters.
 By analyzing state-level polling trends, our model predicts that Kamala Harris is likely to secure key states, leading to an estimated electoral vote count of 341 for Harris and 197 for Donald Trump.
@@
 This is important because accurate election forecasts help reduce uncertainty, which allows political stakeholders to allocate resources efficiently and gives the public a better understanding of likely outcomes.
-Aggregate polling reduces uncertainty and provides a clearer picture of potential outcomes.
 
@@
 The dataset used for this analysis was obtained from the FiveThirtyEight 2024 U.S.
-Presidential Election Polls [@citedata].
+Presidential Election Polls [@citedata] as of October 30, 2024.
 It consists of polling data for the 2024 general election, covering various polling organizations and methodologies.
@@
 ggplot(cleaned_data, aes(x = end_date, y = pct)) +
-  geom_point(alpha = 0.5) +  # Add points for individual poll data
-  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") +  # Show month and year, with one label per month
+  geom_point(alpha = 0.5, color = "black", size = 1.5) + 
+  geom_smooth(color = "#FF6F61", fill = "#FF6F61", method = "loess", se = TRUE, linetype = "solid", size = 1.2) + 
+  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y", expand = c(0.01, 0.01)) + 
   labs(
@@
   ) +
-  theme_minimal() +  # Use a clean minimal theme
+  theme_minimal(base_size = 10) + 
   theme(
-    plot.title = element_text(hjust = 0.5, size = 14),  # Center and adjust title size
-    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for readability
-  ) +
-  geom_smooth()
+    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
+    axis.text = element_text(color = "gray20"),  # Darker axis text for contrast
+    panel.grid.minor = element_blank()  # Remove minor grid for a cleaner look
+)
 ```
@@
 Each black dot represents an individual poll conducted on a specific date, indicating the percentage of voters who supported Trump in that poll.
-The blue line represents a trendline, smoothing out the individual poll results to show the general trajectory of Trump's support over time.
-
 Initially, Trump's polling percentage appears stable with small fluctuations around 45%.
@@
   labs(x = "Numeric Grade",
-       y = "Count") +
+       y = "Frequency") +
   theme_minimal()
@@
   labs(x = "Transparency Score",
-       y = "Count") +
+       y = "Frequency") +
   theme_minimal()
@@
 By using package `usmap` [@citeusmap], @fig-statemap displays the predicted outcome for each state in the 2024 U.S.
-Presidential Election, with red representing states where Trump is expected to win and blue for those favoring Harris.
-
+Presidential Election.
 It shows Trump gaining support across central and southern states, including Texas and Missouri, which have traditionally leaned Republican.

### 2024-11-04 paper/paper.qmd
finalize paper

@@
 
+```{r}
+#| label: tbl-trump-summary
+#| tbl-cap: "Summary Statistics of Trump's Support Percentage in 2024 Polling Data"
+#| echo: false
+#| warning: false
+
+cleaned_data <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))
+
+summary_table <- cleaned_data %>%
+  summarize(
+    Mean = mean(pct, na.rm = TRUE),
+    Median = median(pct, na.rm = TRUE),
+    Min = min(pct, na.rm = TRUE),
+    Max = max(pct, na.rm = TRUE),
+    Std_Dev = sd(pct, na.rm = TRUE),
+    Count = n()
+  )
+
+kable(summary_table,
+      col.names = c("Mean", "Median", "Min", "Max", "Standard Deviation", "Count"),
+      digits = 2)
+```
+
+@tbl-trump-summary presents the key summary statistics for Trump’s support percentage based on a dataset of 348 polling observations from the 2024 U.S.
+presidential election.
+The mean support level is 46.47%, indicating that, on average, 46.47% of respondents in the polls expressed support for Trump.
+The median value of 47% suggests that half of the polls reported support at or below 47%, while the minimum and maximum values show a wide range of support from 27% to 57.9%, reflecting variability across different polls and regions.
+The standard deviation of 4.73 indicates a moderate spread around the mean, suggesting some diversity in polling results but with a central clustering.
+
 ## Predictor variables
